---
title: "Data Guide for Model Terms"
author: "Emily Pollock"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: 
  html_document:
        toc: true
        toc_depth: 3
        toc_float: true
        number_sections: true
        code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ergm.ego)
library(tidyverse)
library(reshape2)
library(srvyr)
library(plotly)
library(kableExtra)
```

```{r import-data}
# want the wide data for degree-related 
egodat <- readRDS("~/nsfg_data_cleaning/Objects/fullEgodata.rds")

egosvy <- as_survey_design(egodat$egos, ids=ego, weights = weight)
##### make ego data objects #########
## mar/coh
datMarcoh <- egodata(egos=egodat$egos, alters=egodat$altersMarCoh, egoWt = egodat$egos$weight, egoIDcol = "ego")
## others 
datOther <- egodata(egos=egodat$egos, alters=egodat$altersOther, egoWt = egodat$egos$weight, egoIDcol = "ego")
## one times 
#datOTs <- egodata(egos=egodat$egos, alters=egodat$altersOnce, egoWt = egodat$egos$weight, egoIDcol = "ego")
# want the long data for absdiff age, sex 
# this data exclusively contains relationships - no inactive egos 
long <- readRDS("~/nsfg_data_cleaning/Objects/altersegos_survdat.rds")
longsvy <- as_survey_design(long,  ids=ego, weights = weight)
```

# Degree Dist {.tabset .tabset-pills .tabset-fade}
## Overall 
```{r}
degs <- egosvy %>% 
        mutate(sex=as.factor(sex), deg.marcoh=as.factor(deg.marcoh), deg.other=as.factor(deg.other)) %>%
        group_by(sex, deg.marcoh, deg.other, .drop = FALSE) %>% 
        summarize(n = survey_total()) %>% 
        group_by(sex) %>%
        mutate(prop = n/sum(n))

fdeg <- degs %>% 
          filter(sex=="F") %>% 
          select(-n, -n_se) %>% 
          pivot_wider(names_from = deg.other, values_from=prop) 
fdeg <- fdeg[,-1]

mdeg <- degs %>% 
          filter(sex=="M") %>% 
          select(-n, -n_se) %>% 
          pivot_wider(names_from = deg.other, values_from=prop) 
mdeg <- mdeg[,-1]

kable(fdeg, col.names = c("Degree Marcoh", "Deg Other=0", "Deg Other=1", "Deg Other=2", "Deg Other=3"),
      caption="Females") %>% kable_styling(full_width = F)

kable(mdeg, col.names = c("Degree Marcoh", "Deg Other=0", "Deg Other=1", "Deg Other=2", "Deg Other=3"),
      caption="Males") %>% kable_styling(full_width = F)
```

## Marriage / Cohabs  
Takeaways:  
 - Fs in fewer marriage/cohabs than men likely due to age boundary 45  
 - important heterogeneity by race (lower among black and others), age  
 - hispanic/white look similar  
```{r marcoh-agesex}
marcoh <- egosvy %>% 
        mutate(sex=as.factor(sex), deg.marcoh=as.factor(deg.marcoh), age=as.factor(age)) %>%
        group_by(sex, age, deg.marcoh, .drop = FALSE) %>% 
        summarize(n = survey_total()) %>% 
        group_by(sex, age) %>%
        mutate(prop = n/sum(n)) %>%
        filter(deg.marcoh==1) %>%
        select(-n, -n_se) %>%
        ggplot(aes(x=age, y=prop, fill=sex)) +
        geom_col(position="dodge") +
        ggtitle("Mean Degree of Marriage/Cohab by Sex & Age")
ggplotly(marcoh)
```

```{r degdist, out.width="50%", out.height="50%", fig.show='hold'}
degreedist(datMarcoh)

degreedist(datMarcoh, by="sex")

degreedist(datMarcoh, by="race")

degreedist(datMarcoh, by="agecat")
```

```{r age-degdist}
degreedist(datMarcoh, by="age")
```

## Casual  
Takeaways: 
 - important heterogeneity by race (higher in black, lower in others), age  
 - hispanic/white looks similar  
 - very small sex differences - age boundary not as much an issue here  
 
```{r casdist}
casual <- egosvy %>% 
        mutate(sex=as.factor(sex), deg.other=as.factor(deg.other), age=as.factor(age)) %>%
        group_by(sex, age, deg.other, .drop = FALSE) %>% 
        summarize(n = survey_total()) %>% 
        group_by(sex, age) %>%
        mutate(prop = n/sum(n)) %>%
        filter(deg.other != 0) %>%
        select(-n, -n_se) %>%
        ggplot(aes(x=age, y=prop, fill=sex)) +
        geom_col(position="dodge") +
        facet_wrap(~deg.other)
        ggtitle("Mean Degree of Casual by Sex & Age")
ggplotly(casual)
```

```{r degdist2, echo=FALSE, out.width="50%", out.height="50%", fig.show='hold'}

degreedist(datOther)

degreedist(datOther, by="sex")

degreedist(datOther, by="race")

degreedist(datOther, by="agecat")
```

## Concurrency
```{r conc}
# two types
# 1: between-network (marriage/cohab & casual)
# 2: intra-netwokr (casual & casual)

egosvy %>% 
        mutate(sex=as.factor(sex), deg.other=as.factor(deg.other>=1), deg.marcoh = as.factor(deg.marcoh), age=as.factor(age)) %>%
        group_by(sex, age, deg.marcoh, deg.other, .drop = FALSE) %>% 
        summarize(n = survey_total()) %>% 
        group_by(sex, age) %>%
        mutate(prop = n/sum(n)) %>%
        filter(deg.other == TRUE & deg.marcoh != 0) %>%
        select(-n, -n_se) %>%
        ggplot(aes(x=age, y=prop, fill=sex)) +
        geom_col(position="dodge") +
        ggtitle("proportion of egos w/ between-network concurrency by sex & age")


bet <- egosvy %>% 
        mutate(sex=as.factor(sex), deg.other=as.factor(deg.other>=1), deg.marcoh = as.factor(deg.marcoh), age=as.factor(age)) %>%
        group_by(sex, age, deg.marcoh, deg.other, .drop = FALSE) %>% 
        summarize(n = survey_total()) %>% 
        group_by(sex, age) %>%
        mutate(prop = n/sum(n)) %>%
        filter(deg.other == TRUE & deg.marcoh != 0) %>%
        select(-n, -n_se) %>%
        group_by(sex) %>%
        mutate(mean=mean(prop, na.rm = T))

means <- data.frame(Sex = c("Females", "Males"), Mean = unique(bet$mean))

kable(means, caption = "Mean proportion of egos w/ cross-network concurrency by sex") %>%
  kable_styling(full_width = F)

raceconc1 <- egosvy %>% 
        mutate(sex=as.factor(sex), race=as.factor(race), deg.other=as.factor(deg.other>=1), deg.marcoh = as.factor(deg.marcoh), age=as.factor(age)) %>%
        group_by(sex, race, deg.other, deg.marcoh, .drop = FALSE) %>% 
        summarize(n = survey_total()) %>% 
        group_by(sex, race) %>%
        mutate(prop = n/sum(n)) %>%
        filter(deg.other == TRUE & deg.marcoh != 0) %>%
        select(-n, -n_se) %>%
        ggplot(aes(x=race, y=prop, fill=sex)) +
        geom_col(position="dodge") +
        ggtitle("Prop egos w/ cross-network concurrency by race")
ggplotly(raceconc1)


egosvy %>% 
        mutate(sex=as.factor(sex), deg.other=as.factor(deg.other>=2), age=as.factor(age)) %>%
        group_by(sex, age, deg.other, .drop = FALSE) %>% 
        summarize(n = survey_total()) %>% 
        group_by(sex, age) %>%
        mutate(prop = n/sum(n)) %>%
        filter(deg.other == TRUE) %>%
        select(-n, -n_se) %>%
        ggplot(aes(x=age, y=prop, fill=sex)) +
        geom_col(position="dodge") +
        ggtitle("proportion of egos w/ within-casual-network concurrency by sex & age")


int <- egosvy %>% 
        mutate(sex=as.factor(sex), deg.other=as.factor(deg.other>1), age=as.factor(age)) %>%
        group_by(sex, age, deg.other, .drop = FALSE) %>% 
        summarize(n = survey_total()) %>% 
        group_by(sex, age) %>%
        mutate(prop = n/sum(n)) %>%
        filter(deg.other == TRUE) %>%
        select(-n, -n_se) %>%
        group_by(sex) %>%
        mutate(mean=mean(prop, na.rm = T))

means <- data.frame(Sex = c("Females", "Males"), Mean = unique(int$mean))

kable(means, caption = "Mean proportion of egos w/ casual-network concurrency by sex") %>%
  kable_styling(full_width = F)

raceconc <- egosvy %>% 
        mutate(sex=as.factor(sex), race=as.factor(race), deg.other=as.factor(deg.other>1), age=as.factor(age)) %>%
        group_by(sex, race, deg.other, .drop = FALSE) %>% 
        summarize(n = survey_total()) %>% 
        group_by(sex, race) %>%
        mutate(prop = n/sum(n)) %>%
        filter(deg.other == TRUE) %>%
        select(-n, -n_se) %>%
        ggplot(aes(x=race, y=prop, fill=sex)) +
        geom_col(position="dodge") +
        ggtitle("Prop egos w/ casual concurrency by race")
ggplotly(raceconc)
```

# Age Mixing 
## Marriages / Cohabs {.tabset .tabset-pills .tabset-fade}
### Diff Age
```{r age-marcoh, echo=FALSE, fig.align="center", warning=FALSE, message=FALSE}
agediff <- longsvy %>% 
  filter(active==1, network1=="marcoh") %>%
  mutate(sqrtdiff = e.age-age) %>%
  mutate(age=as.factor(e.age), sex=as.factor(e.sex)) %>%
  group_by(e.age, e.sex) %>% 
  summarize(n=survey_mean(sqrtdiff))

agediff %>% 
  ggplot(aes(x=e.age, y=n)) +
  geom_point() +
  facet_wrap(~e.sex) + 
  geom_hline(yintercept = 0)
```

### Diff Sqrt Age  
```{r sqrtage-other, echo=FALSE, fig.align="center", warning=FALSE, message=FALSE}
sqrtagediff <- longsvy %>% 
  filter(active==1, network1=="marcoh") %>%
  mutate(sqrtdiff = sqrt(e.age)-sqrt(age)) %>%
  mutate(age=as.factor(e.age), sex=as.factor(e.sex)) %>%
  group_by(e.age, e.sex) %>% 
  summarize(n=survey_mean(sqrtdiff))

sqrtagediff %>% 
  ggplot(aes(x=e.age, y=n)) +
  geom_point() +
  facet_wrap(~e.sex) + 
  geom_hline(yintercept = 0)

sexmean <- longsvy %>% 
  filter(active==1, network3=="mar") %>%
  mutate(sqrtdiff = sqrt(e.age)-sqrt(age)) %>%
  mutate(age=as.factor(e.age), sex=as.factor(e.sex)) %>%
  group_by(e.sex) %>% 
  summarize(n=survey_mean(sqrtdiff)) 

sexmean %>%
  kable() %>%
  kable_styling()

shift <- mean(abs(sexmean$n))
shift

sexmean <- longsvy %>% 
  filter(active==1, network3=="cohab") %>%
  mutate(sqrtdiff = sqrt(e.age)-sqrt(age)) %>%
  mutate(age=as.factor(e.age), sex=as.factor(e.sex)) %>%
  group_by(e.sex) %>% 
  summarize(n=survey_mean(sqrtdiff)) 

sexmean %>%
  kable() %>%
  kable_styling()

shift <- mean(abs(sexmean$n))
shift
```

### Diff Cube Root Age
```{r cbage-other, echo=FALSE, fig.align="center", warning=FALSE, message=FALSE}
cbagediff <- longsvy %>% 
  filter(active==1, network1=="other") %>%
  mutate(cbdiff = (e.age^(1/3)) - (age^(1/3))) %>%
  mutate(age=as.factor(e.age), sex=as.factor(e.sex)) %>%
  group_by(e.age, e.sex) %>% 
  summarize(n=survey_mean(cbdiff))

cbagediff %>% 
  ggplot(aes(x=e.age, y=n)) +
  geom_point() +
  facet_wrap(~e.sex) + 
  geom_hline(yintercept = 0)
```

## Others {.tabset .tabset-pills .tabset-fade}
### Diff Age
```{r age-marcoh, echo=FALSE, fig.align="center", warning=FALSE, message=FALSE}
agediff <- longsvy %>% 
  filter(active==1, network1=="marcoh") %>%
  mutate(sqrtdiff = e.age-age) %>%
  mutate(age=as.factor(e.age), sex=as.factor(e.sex)) %>%
  group_by(e.age, e.sex) %>% 
  summarize(n=survey_mean(sqrtdiff))

agediff %>% 
  ggplot(aes(x=e.age, y=n)) +
  geom_point() +
  facet_wrap(~e.sex) + 
  geom_hline(yintercept = 0)
```

### Diff Sqrt Age  
```{r sqrtage-marcoh, echo=FALSE, fig.align="center", warning=FALSE, message=FALSE}
sqrtagediff <- longsvy %>% 
  filter(active==1, network3=="mar") %>%
  mutate(sqrtdiff = sqrt(e.age)-sqrt(age)) %>%
  mutate(age=as.factor(e.age), sex=as.factor(e.sex)) %>%
  group_by(e.age, e.sex) %>% 
  summarize(n=survey_mean(sqrtdiff))

sqrtagediff %>% 
  ggplot(aes(x=e.age, y=n)) +
  geom_point() +
  facet_wrap(~e.sex) + 
  geom_hline(yintercept = 0)

sexmean <- longsvy %>% 
  filter(active==1, network3=="casual") %>%
  mutate(sqrtdiff = sqrt(e.age)-sqrt(age)) %>%
  mutate(age=as.factor(e.age), sex=as.factor(e.sex)) %>%
  group_by(e.sex) %>% 
  summarize(n=survey_mean(sqrtdiff)) 

sexmean %>%
  kable() %>%
  kable_styling()

shift <- mean(abs(sexmean$n))
shift
```

### Diff Cube Root Age
```{r cbage-marcoh, echo=FALSE, fig.align="center", warning=FALSE, message=FALSE}
cbagediff <- longsvy %>% 
  filter(active==1, network1=="marcoh") %>%
  mutate(cbdiff = (e.age^(1/3)) - (age^(1/3))) %>%
  mutate(age=as.factor(e.age), sex=as.factor(e.sex)) %>%
  group_by(e.age, e.sex) %>% 
  summarize(n=survey_mean(cbdiff))

cbagediff %>% 
  ggplot(aes(x=e.age, y=n)) +
  geom_point() +
  facet_wrap(~e.sex) + 
  geom_hline(yintercept = 0)
```

### One-Times

this needs some work 

```{r agemixing-onetimes, eval=F}
agemixF <- round(mixingmatrix(datOTs[datOTs$egos$sex %in% "F"], "agecat", rowprob = T), 3)
agemixF <- agemixF[1:6,]
amF <- melt(agemixF)
amF$sex <- "F"

agemixM <- round(mixingmatrix(datOTs[datOTs$egos$sex %in% "M"], "agecat", rowprob = T), 3)
agemixM <- agemixM[1:6,]
amM <- melt(agemixM)
amM$sex <- "M"

am <-  rbind(amF, amM)

am %>% ggplot(aes(ego, alter)) + 
  geom_point(color="blue", alpha=0.2, aes(size=value)) +
  scale_size_area(max_size = 30) +
  geom_text(aes(label=round(value,2), size=0.015)) +
  theme(legend.position="none",
        axis.text.x = element_text(angle=45)) +
  coord_flip() +
  labs(title = "Age Mixing - One-Times") +
  facet_wrap(~sex, ncol = 2)
```

## Race Mixing 

### Mar/Cohs
```{r race-mixing-marcoh, echo=FALSE, fig.align="center"}
racemixF <- round(mixingmatrix(datMarcoh[datMarcoh$egos$sex %in% "F"], "race", rowprob = T), 3)
rmF <- melt(racemixF)
rmF$sex <- "F"

racemixM <- round(mixingmatrix(datMarcoh[datMarcoh$egos$sex %in% "M"], "race", rowprob = T), 3)
rmM <- melt(racemixM)
rmM$sex <- "M"

rm <-  rbind(rmF, rmM)

rm %>% ggplot(aes(ego, alter)) + 
  geom_point(color="springgreen3", alpha=0.3, aes(size=value)) +
  scale_size_area(max_size = 30) +
  geom_text(aes(label=round(value,2), size=0.015)) +
  theme(legend.position="none") +
  coord_flip() +
  labs(title = "Race Mixing - All Active Mar/Coh") +
  facet_wrap(~sex, ncol = 2)
```

### Other
```{r race-mixing-other, echo=FALSE, fig.align="center"}
racemixF <- round(mixingmatrix(datOther[datOther$egos$sex %in% "F"], "race", rowprob = T), 3)
rmF <- melt(racemixF)
rmF$sex <- "F"

racemixM <- round(mixingmatrix(datOther[datOther$egos$sex %in% "M"], "race", rowprob = T), 3)
rmM <- melt(racemixM)
rmM$sex <- "M"

rm <-  rbind(rmF, rmM)

rm %>% ggplot(aes(ego, alter)) + 
  geom_point(color="springgreen3", alpha=0.3, aes(size=value)) +
  scale_size_area(max_size = 30) +
  geom_text(aes(label=round(value,2), size=0.015)) +
  theme(legend.position="none") +
  coord_flip() +
  labs(title = "Race Mixing - All Active Others") +
  facet_wrap(~sex, ncol = 2)
```

## One-Times 

one-times based on Male egos reports of partner race if one-time partner was most recent 
female one-times partner race based on male reports 

```{r racemix-onetimes, echo=FALSE, eval=F}
racemixM <- round(mixingmatrix(datOTs[datOTs$egos$sex %in% "M"], "race", rowprob = T), 3)
rmM <- melt(racemixM)
rmM$sex <- "M"

racemixMcounts<- mixingmatrix(datOTs[datOTs$egos$sex %in% "M"], "race")
racemixFcounts <- t(racemixMcounts)
racemixF <- round(racemixFcounts/rowSums(racemixFcounts),3) 
rmF <- melt(racemixF)
colnames(rmF) <- c("ego", "alter", "value")
rmF$sex <- "F"

rm <-  rbind(rmF, rmM)

rm %>% ggplot(aes(ego, alter)) + 
  geom_point(color="blue", alpha=0.2, aes(size=value)) +
  scale_size_area(max_size = 30) +
  geom_text(aes(label=round(value,2), size=0.015)) +
  theme(legend.position="none") +
  coord_flip() +
  labs(title = "Race Mixing - One-Times") +
  facet_wrap(~sex, ncol = 2)
```

