---
title: "Testing Parameters"
author: "Emily Pollock"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
    html_document:
        toc: true
        toc_depth: 3
        toc_float: true
        number_sections: true
        code_folding: hide
---

```{r setup, message=F, warning=F}
library(here)
#library(flexsurv)
library(srvyr)
library(kableExtra)
library(tidyverse)
library(survey)

# objects
dat <- readRDS("~/nsfg_data_cleaning/Objects/egos.rds")
svy <- as_survey_design(dat, ids = ego, weights = weight)
```

# Chlamydia Test in last year {.tabset}
(conditional on being a female who has had a sex parter in last year)

## Age Category
```{r agecat}
prop_women_tested_agecat <- svy %>% 
                      filter(sex == "F", CHLAMTST <9, partsyr3 > 0) %>% 
                      mutate(CHLAMTST = as.factor(CHLAMTST)) %>% 
                      group_by(agecat, CHLAMTST) %>% 
                      survey_tally() %>% 
                      mutate(prop=n/sum(n)) %>%
                      filter(CHLAMTST==1)

mean2 <- mean(prop_women_tested_agecat$prop)

prop_women_tested_agecat %>% ggplot() +
  geom_point(aes(x=agecat, y=prop)) 
```

## Int. Year
```{r intyr}
prop_women_tested_year <- svy %>% 
                      filter(sex == "F", CHLAMTST <9, partsyr3 >0) %>% 
                      mutate(CHLAMTST = as.factor(CHLAMTST), 
                             intyr = as.factor(intyr)) %>%
                      group_by(intyr, CHLAMTST) %>% 
                      survey_tally() %>% 
                      mutate(prop=n/sum(n)) %>%
                      filter(CHLAMTST %in% 1)

mean <- mean(prop_women_tested_year$prop)

prop_women_tested_year %>% ggplot() +
  geom_point(aes(x=intyr, y=prop)) + 
  geom_smooth(aes(x=intyr, y=prop))
```

## Point Estimates - AgeCat 
```{r chlam}
tab <- prop_women_tested_agecat[,c(1,5)]
tab$prop <- round(tab$prop, 3)

kable(tab, caption="Proportion of Sexually Active Women who Tested in Last Year") %>%
  kable_styling()
```

# Sex Acts per Time Step

because "sex4wk" is an aggregate variable, not a dyad-specific variable, we may overestimate 

solution - modify sex4wk by # active partners? so 20 acts / month for monogamous , but 10 acts/month if they had 2 partners? is that even a reasonable assumption? That's what we do here per chat w/ SMG 3/18/21

```{r prep-data, echo=F}
# objects
dyad <- readRDS("~/nsfg_data_cleaning/Objects/altersegos_survdat.rds")
# convert duration from months to weeks
dyad <- dyad %>% 
  filter(active==1) %>%
  mutate(edge_age_week = edge_age_month/12*52,
        t_o_week = t_o/12*52,
        t_c_week = t_c/12*52)

# add sex4wk and cond4wk based on ego report
egos <- dyad$ego
sex <- dat$sex4wk[egos]
cond <- dat$cond4wk[egos]

dyad$sex4wk <- sex
dyad$cond4wk <- cond 

data <- dyad %>%
  filter(sex4wk<900 & cond4wk <900) %>%
  mutate(comb.age = age + e.age) %>%
  mutate(ptype=ifelse(network1 %in% "marcoh", 1, 2)) %>%
  mutate(duration=edge_age_week)

# don't need to use svyglm - SE will be different, but predictions the same (and glm is base R so easier to use in simulations)
#svydyad <- as_survey_design(dyad, ids = ego, weights = weight)
#actsMonth <- svyglm(sex4wk  ~comb.age + network1 + edge_age_week, family = "poisson", design=svydyad) 
#predict1 <- predict(actsMonth, svydyad)

actives3ego <- egos[table(egos)==3]
actives2ego <- egos[table(egos)==2]

data2 <- data
data2$sex4wk[data$ego %in% actives3ego] <- round(data2$sex4wk[data$ego %in% actives3ego]/3)
data2$sex4wk[data$ego %in% actives2ego] <- round(data2$sex4wk[data$ego %in% actives2ego]/2)

# do this for condom use too 
data2$cond4wk[data$ego %in% actives3ego] <- round(data2$cond4wk[data$ego %in% actives3ego]/3)
data2$cond4wk[data$ego %in% actives2ego] <- round(data2$cond4wk[data$ego %in% actives2ego]/2)

data2$nocond <- data2$sex4wk-data2$cond4wk 
data2 <- data2 %>% filter(nocond>=0) 

svydat <- as_survey_design(data2, id=ego, weights=weight) 
```

## Univariate {.tabset}
### Combined Age 
```{r acts.age}
acts.age <- svyglm(sex4wk ~ comb.age, family = "poisson", design=svydat)
acts.age2 <- svyglm(sex4wk ~ comb.age + I(comb.age^2), family = "poisson", design=svydat) 
summary(acts.age)
AIC(acts.age)
summary(acts.age2)
AIC(acts.age2)
```

### Partnership Type
```{r acts.ptype}
acts.ptype <- svyglm(sex4wk ~ ptype, family = "poisson", design=svydat) 
summary(acts.ptype)
```

### Current Relationship Duration
```{r acts.dur}
acts.dur <- svyglm(sex4wk ~ duration, family = "poisson", design=svydat) 
summary(acts.dur)
```

## Multivariate 
```{r acts.full, echo=F}
acts.full <- svyglm(sex4wk ~ comb.age + ptype, family = "poisson", design=svydat) 
acts.full2 <- svyglm(sex4wk ~ comb.age + I(comb.age^2) + ptype, family = "poisson", design=svydat) 
summary(acts.full)
summary(acts.full2)
```

## Output for Epimodel
```{r acts, echo=F}
acts.mod <- glm(sex4wk ~ comb.age + I(comb.age^2) + ptype, 
                family = "poisson", 
                weights=data2$weight, 
                data=data2) 

#rates2 <- unname(predict(acts.mod, data2, type = "response"))/4
#acts2 <- rpois(length(rates2), rates2)
```

# Condom use per act - Marcoh & Other

## Multivariate {.tabset}
### w/o Duration
```{r condoms-fullnoduration}
c.svy.fullnodur <- svyglm(formula = cbind(cond4wk, sex4wk-cond4wk) ~ comb.age + ptype, 
               family=binomial, design=svydat) 
summary(c.svy.fullnodur)
```
### w/ Duration 
```{r condoms-fullduration}
c.svy.fulldur <- svyglm(formula = cbind(cond4wk, sex4wk-cond4wk) ~ comb.age + ptype + duration, 
               family=binomial, design=svydat) 
summary(c.svy.fulldur)
```

## Univariate {.tabset}
### Combined Age 
```{r condoms-age}
c.svy.comb.age <- svyglm(formula = cbind(cond4wk, sex4wk-cond4wk) ~ comb.age, 
               family=binomial, design=svydat) 
summary(c.svy.comb.age)
```
### Partership Type
```{r condoms-ptype}
c.svy.ptype <- svyglm(formula = cbind(cond4wk, sex4wk-cond4wk) ~ ptype, 
               family=binomial, design=svydat) 
summary(c.svy.ptype)
```

## Output for EpiModel

```{r, echo=F}
condom.mod <- glm(formula = cbind(cond4wk, sex4wk-cond4wk) ~ comb.age + I(comb.age^2) + ptype, 
               family = "binomial", weights=data2$weight, data=data2) 

#probs <- unname(predict(condoms, data, type = "response"))
#condom.use <- rbinom(length(probs), 1, probs)
```

# Condom use per act - Inst
in nsfg, only females asked if they used condom at last sex
here we pull probability that females report using condom using "once" encounters
note: of the 168 inst encounters in data, 19 are reported by females
```{r inst}
once <- data2 %>% filter(once==1)
mean(once$condls, na.rm=T)
```

## Make list for EpiModel
```{r epistats}
epistats <- list(acts.mod, condom.mod)
saveRDS(epistats, here("prep", "epistats.rds"))
```