---
title: "Network Fitting"
author: "Emily Pollock"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
    html_document:
        toc: true
        toc_depth: 3
        toc_float: true
        number_sections: true
        code_folding: hide
---

```{r setup, include=FALSE}
library(ergm.ego)
library(EpiModel)
library(parallel)
library(egonet)
library(here)
source("~/Documents/Dissertation/R/Duration/Functions/finalEgodataPrep.R") # generates the egodata objects
source("~/Documents/Dissertation/R/EPT/prep/setup_params.R") # object with params of interest 
```

# Session Info
```{r}
sessioninfo::package_info()
```

# General Controls  

__need to update duration targets w/ estimated means from parametric model__  
__but then will also need to use CKs correction in-simiulation find undelrying relationship length in presense of mortality__  
```{r}
np <- detectCores()
# Set parallel.type
if (np==0) ptype=NULL else ptype='PSOCK'

dat <- setup_params()
ppopsize <- dat$ppopsize
MCMCinterval <- dat$mcmcInterval
MCMCburnin <- dat$mcmcBurnin

time.step <- dat$time.step
age.width <- dat$age.width
dissolution <- dat$dissolution
#mRate <- dat$mRate

duration.mar <- dat$duration.marriage
duration.cohab <- dat$duration.cohab
duration.other <- dat$duration.other

DissolutionMar <- dissolution_coefs(dissolution=dissolution, 
                                       duration=duration.mar)

DissolutionCohab <- dissolution_coefs(dissolution=dissolution, 
                                       duration=duration.cohab)

DissolutionOther <- dissolution_coefs(dissolution=dissolution, 
                                      duration=duration.other)
```

# Some Adjustments  
* make age/sex attribute (i.e. 15F, 23M)  
* sample down to 10,000  

```{r}
ssize <- 10000
# sample down to 10,000
egodat_marriage <- sample(egodat_marriage, ssize)

# pull sampled egos, attribute updates, and update other alter lists (for consistent nodeset)
egos <- egodat_marriage$egos

egodat_cohab$alters <- egodat_cohab$alters[egodat_cohab$alters$ego %in% egos$ego,]
egodat_other$alters <- egodat_other$alters[egodat_other$alters$ego %in% egos$ego,]
egodat_once$alters <- egodat_once$alters[egodat_once$alters$ego %in% egos$ego,]

egos$ageF <- ifelse(egos$male==0, egos$age, 0)
egos$ageM <- ifelse(egos$male==1, egos$age, 0)

egodat_marriage$alters$ageF <- ifelse(egodat_marriage$alters$male==0, egodat_marriage$alters$age, 0)
egodat_marriage$alters$ageM <- ifelse(egodat_marriage$alters$male==1, egodat_marriage$alters$age, 0)

egodat_cohab$alters$ageF <- ifelse(egodat_cohab$alters$male==0, egodat_cohab$alters$age, 0)
egodat_cohab$alters$ageM <- ifelse(egodat_cohab$alters$male==1, egodat_cohab$alters$age, 0)

egodat_other$alters$ageF <- ifelse(egodat_other$alters$male==0, egodat_other$alters$age, 0)
egodat_other$alters$ageM <- ifelse(egodat_other$alters$male==1, egodat_other$alters$age, 0)

egodat_once$alters$ageF <- ifelse(egodat_once$alters$male==0, egodat_once$alters$age, 0)
egodat_once$alters$ageM <- ifelse(egodat_once$alters$male==1, egodat_once$alters$age, 0)

egodat_marriage$egos <- egos
egodat_cohab$egos <- egos
egodat_other$egos <- egos
egodat_once$egos <- egos

egodat_cohab$egoWt <- egodat_marriage$egoWt
egodat_other$egoWt <- egodat_marriage$egoWt
egodat_once$egoWt <- egodat_marriage$egoWt


# grab binary deg dist for plots below, x2 for scaline to 20000 nodes
m <- with(egodat_marriage$egos[egodat_marriage$egos$male==1,], table(age, deg.mar))
m <- m[,2]*(ppopsize/ssize)
f <- with(egodat_marriage$egos[egodat_marriage$egos$male==0,], table(age, deg.mar))
f <- f[,2]*(ppopsize/ssize)

mc <- with(egodat_cohab$egos[egodat_cohab$egos$male==1,], table(age, deg.cohab))
mc <- mc[,2]*(ppopsize/ssize)
fc <- with(egodat_cohab$egos[egodat_cohab$egos$male==0,], table(age, deg.cohab))
fc <- fc[,2]*(ppopsize/ssize)

mo <- with(egodat_other$egos[egodat_other$egos$male==1,], table(age, deg.other))
mo <- mo[,2]*(ppopsize/ssize)
fo <- with(egodat_other$egos[egodat_other$egos$male==0,], table(age, deg.other))
fo <- fo[,2]*(ppopsize/ssize)

saveRDS(list(egodat_marriage, egodat_cohab, egodat_other, egodat_once), here("fits", "egodata.rds"))
x <- readRDS(here("fits", "egodata.rds"))
egodat_marriage <- x[[1]]
egodat_cohab <- x[[2]]
egodat_other <- x[[3]]
egodat_once <- x[[4]]
```

# Marriage Network {.tabset .tabset-pills .tabset-fade}

## Ergm.Ego Estimation & Setup

```{r, eval=F}
dat$shift.mar

fit.marriage <- ergm.ego(egodat_marriage ~ edges + 
                         nodecov(~ageF) + 
                         nodecov(~ageF^2) +
                         nodecov(~ageF<30) + 
                         nodecov(~ageF>30) +
                         nodecov(~ageM) + 
                         nodecov(~ageM^2) +
                         nodecov(~ageM<30) + 
                         nodecov(~ageM>30) + 
                         absdiff(~sqrtage + 0.1390122*(male==0)) + 
                         nodefactor("deg.other.binary") +
                         offset(nodematch("male", diff = FALSE)) +
                         offset(nodefactor("olderpartnerM")) +
                         offset(nodefactor("deg.cohab")) +
                         offset("concurrent"), 
                         offset.coef = c(-Inf, -Inf, -Inf, -Inf), 
                         control = 
                         control.ergm.ego(ppop.wt = "sample", ppopsize = ppopsize, 
                                          ergm.control = 
                                            control.ergm(MCMLE.maxit = 100,
                                                         MCMC.interval = MCMCinterval, 
                                                         MCMC.burnin = MCMCburnin,
                                                         parallel = np,
                                                         parallel.type = ptype)))

#offset(nodefactor("debuted", levels=1)) + 
#nodefactor(~ageF, levels=5:9) + 
#nodefactor(~ageM, levels=7:10) + 

saveRDS(fit.marriage, here("fits", "fit.marriage.rds"))
```

```{r}
fit.marriage <- readRDS(here("fits", "fit.marriage.rds"))
mpop <- environment(fit.marriage$ergm.formula)$popnw
marriage.netest <- ego.netest(fit.marriage, DissolutionMar)
summary(fit.marriage)
```

## MCMC Diagnostics / GOF
```{r, warning=F, message=F, comment = F, results='hide', fig.keep='all'}
mcmc.diagnostics(fit.marriage)
```

```{r, eval=F}
gof <- gof(fit.marriage, GOF = "model")
saveRDS(gof, here("fits", "gof.m.rds"))
```

```{r}
gof <- readRDS(here("fits", "gof.m.rds"))
plot(gof)
```

## Static Diagnostics 

```{r, eval=F}
static.mar <- netdx(marriage.netest, nsims = 500, dynamic = FALSE)
saveRDS(static.mar, here("fits", "static.m.rds"))
```

```{r}
static.mar <- readRDS(here("fits", "static.m.rds"))
static.mar
plot(static.mar)
```

## Dynamic Diagnostics 
```{r, eval=F}
dynamic.marriage <- netdx(marriage.netest, nsims = 5, nsteps = 1000, ncores = np, 
                       set.control.ergm = control.simulate.ergm(MCMC.burnin=1e5, 
                                                                MCMC.interval=1e5),
                       set.control.stergm = control.simulate.network(MCMC.burnin.min=1e5,
                                                                     MCMC.burnin.max=1e5))
saveRDS(dynamic.marriage, here("fits", "dynamic.m.rds"))
```

```{r}
dynamic.marriage <- readRDS(here("fits", "dynamic.m.rds"))
dynamic.marriage
plot(dynamic.marriage)
plot(dynamic.marriage, type = "duration")
plot(dynamic.marriage, type = "dissolution")
```


## Checking Mean Deg Dist by Age/Sex and Age/Sex Mixing are close to data 
```{r diag-diagnostic-mar}
n <- dynamic.marriage$nw

plot(summary(n ~ nodefactor(~ageM)), type="l", main="Males")
lines(m, pch=19, col="blue")
legend("topright", legend = c("Empirical", "Model"), col=c("blue", "black"), lwd=1)

plot(summary(n ~ nodefactor(~ageF)), type="l", main="Females")
lines(f, col="blue")
legend("topright", legend = c("Empirical", "Model"), col=c("blue", "black"), lwd=1)

# age/sex mixing
aF <- n %v% "ageF"
aM <- n %v% "ageM" 

el <- as.edgelist(n)
fem1 <- aF[el[,1]]
fem2 <- aF[el[,2]]
male1 <- aM[el[,1]]
male2 <- aM[el[,2]]

allFs <- NULL
allMs <- NULL 

for (i in 1:length(fem1)){
  if (fem1[i] != 0) {allFs[i] <- fem1[i]} 
  else {allFs[i] <- fem2[i]}
  
  if (male1[i] != 0) {allMs[i] <- male1[i]} 
  else {allMs[i] <- male2[i]}
  }

agesel <- as.data.frame(cbind(allFs, allMs))
sqrtages <- sqrt(agesel)
sqrtages$diff <- sqrtages[,1] - sqrtages[,2]
mean(sqrtages$diff)
```


# Cohab Network {.tabset .tabset-pills .tabset-fade}

## Ergm.Ego Estimation & Setup

```{r, eval=F}
dat$shift.cohab

x <- control.ergm.ego(ppopsize = 1, ppop.wt = "sample",
                      ergm.control = control.ergm(MCMLE.maxit = 200,
                                                  MCMC.interval = MCMCinterval,
                                                  MCMC.burnin = MCMCburnin))

x$ppopsize <- mpop

fit.cohab <- ergm.ego(egodat_cohab ~ edges + 
                         nodefactor(~ageF, levels=4:10) + 
                         nodefactor(~ageM, levels=5:10) + 
                         nodecov(~ageF) +
                         nodecov(~ageF>=27) +
                         nodecov(~ageM) + 
                         nodecov(~ageM>=27) + 
                         absdiff(~sqrtage + 0.1794225*(male==0)) + 
                         nodefactor("deg.other.binary") +
                         offset(nodematch("male", diff = FALSE)) +
                         offset(nodefactor("olderpartnerC")) +
                         offset(nodefactor("deg.mar")) +
                         offset("concurrent") +
                         offset(nodefactor(~ageF, levels=2:3)) +
                         offset(nodefactor(~ageM, levels=2:4)),
                         offset.coef = c(rep(-Inf, 9)),
                         control = x)

#offset(nodefactor("debuted", levels=1)) + 

saveRDS(fit.cohab, here("fits", "fit.cohab.rds"))
```

```{r}
fit.cohab <- readRDS(here("fits", "fit.cohab.rds"))
cohab.netest <- ego.netest(fit.cohab, DissolutionCohab)
summary(fit.cohab)
```

## MCMC Diagnostics / GOF
```{r, warning=F, message=F, comment = F, results='hide', fig.keep='all'}
mcmc.diagnostics(fit.cohab)
```

```{r, eval=F}
gof <- gof(fit.cohab, GOF = "model")
saveRDS(gof, here("fits", "gof.c.rds"))
```

```{r}
gof <- readRDS(here("fits", "gof.c.rds"))
plot(gof)
```

## Static Diagnostics 

```{r, eval=F}
static.cohab <- netdx(cohab.netest, nsims = 500, dynamic = FALSE)
saveRDS(static.cohab, here("fits", "static.c.rds"))
```

```{r}
static.cohab <- readRDS(here("fits", "static.c.rds"))
static.cohab
plot(static.cohab)
```

## Dynamic Diagnostics 
```{r, eval=F}
dynamic.cohab <- netdx(cohab.netest, nsims = 5, nsteps = 1000, ncores = np, 
                       set.control.ergm = control.simulate.ergm(MCMC.burnin=1e5, 
                                                                MCMC.interval=1e5),
                       set.control.stergm = control.simulate.network(MCMC.burnin.min=1e5,
                                                                     MCMC.burnin.max=1e5))
saveRDS(dynamic.cohab, here("fits", "dynamic.c.rds"))
```

```{r}
dynamic.cohab <- readRDS(here("fits", "dynamic.c.rds"))
plot(dynamic.cohab)
plot(dynamic.cohab)
plot(dynamic.cohab, type = "duration")
plot(dynamic.cohab, type = "dissolution")
```


## Checking Mean Deg Dist by Age/Sex and Age/Sex Mixing are close to data 
```{r diag-diagnostic-cohab, out.width="70%"}
n <- dynamic.cohab$nw

plot(summary(n ~ nodefactor(~ageM)), type="l", main="Males")
lines(mc, pch=19, col="blue")
legend("topright", legend = c("Empirical", "Model"), col=c("blue", "black"), lwd=1)

plot(summary(n ~ nodefactor(~ageF)), type="l", main="Females")
lines(fc, col="blue")
legend("topright", legend = c("Empirical", "Model"), col=c("blue", "black"), lwd=1)

# age/sex mixing
aF <- n %v% "ageF"
aM <- n %v% "ageM" 

el <- as.edgelist(n)
fem1 <- aF[el[,1]]
fem2 <- aF[el[,2]]
male1 <- aM[el[,1]]
male2 <- aM[el[,2]]

allFs <- NULL
allMs <- NULL 

for (i in 1:length(fem1)){
  if (fem1[i] != 0) {allFs[i] <- fem1[i]} 
  else {allFs[i] <- fem2[i]}
  
  if (male1[i] != 0) {allMs[i] <- male1[i]} 
  else {allMs[i] <- male2[i]}
  }

agesel <- as.data.frame(cbind(allFs, allMs))
sqrtages <- sqrt(agesel)
sqrtages$diff <- sqrtages[,1] - sqrtages[,2]
mean(sqrtages$diff)
```



# Other Network {.tabset .tabset-pills .tabset-fade}

## Fit
```{r, eval=F } 
dat$shift.other

fit.other <- ergm.ego(egodat_other ~ edges + 
                         nodecov(~ageF) + 
                         nodecov(~ageF<19) + 
                         nodecov(~ageF>19) + 
                         nodecov(~ageF^2) +
                         nodecov(~ageM<19) + 
                         nodecov(~ageM>19) + 
                         nodecov(~ageM) + 
                         nodecov(~ageM^2) +
                        absdiff(~sqrtage + 0.14505*(male==0)) + 
                        nodefactor("deg.mar") +
                        nodefactor("deg.cohab") +
                        nodefactor(~ageF %in% 17) +
                        nodefactor(~ageM %in% 17) + 
                        concurrent(by=~male) +
                        offset(nodematch("male", diff = FALSE)) +
                        offset(nodefactor("olderpartnerO")),
                        offset.coef = c(-Inf, -Inf), 
                        control = x)


#offset(nodefactor("debuted", levels=1)),
#offset.coef = c(-Inf, -Inf),

saveRDS(fit.other, here("fits", "fit.other.rds"))
```


```{r}
fit.other <- readRDS(here("fits", "fit.other.rds"))
other.netest <- ego.netest(fit.other, DissolutionOther)
summary(fit.other)
```

## MCMC Diagnostics / GOF
```{r, warning=F, message=F, comment = F, results='hide', fig.keep='all'}
mcmc.diagnostics(fit.other)
```

```{r, eval=F}
gof.o <- gof(fit.other, GOF = "model")
saveRDS(gof.o, here("fits", "gof.o.rds"))
```

```{r}
gof.o <- readRDS(here("fits", "gof.o.rds"))
plot(gof.o)
```

## Static Diagnostic 
```{r }
static.other <- netdx(other.netest, nsims = 500, dynamic = FALSE)
saveRDS(static.other, here("fits", "static.other.rds"))
```

```{r, eval=F}
static.other <- readRDS(here("fits", "static.other.rds"))
static.other
plot(static.other)
```

## Dynamic Diagnostic

```{r, eval=F}
dynamic.other <- netdx(other.netest, nsims = 5, nsteps = 1000, ncores = np,
                       set.control.ergm = control.simulate.ergm(MCMC.burnin=1e5, 
                                                                MCMC.interval=1e5),
                       set.control.stergm = control.simulate.network(MCMC.burnin.min=1e5,
                                                                     MCMC.burnin.max=1e5))
saveRDS(dynamic.other, here("fits", "dynamic.other.rds"))
```

```{r}
dynamic.other <- readRDS(here("fits", "dynamic.other.rds"))
dynamic.other
plot(dynamic.other)
plot(dynamic.other, type = "duration")
plot(dynamic.other, type = "dissolution")
```

## Checking Mean Deg Dist by Age/Sex and Age/Sex Mixing are close to data  
```{r diag-diagnostic, out.width="70%"}
n <- dynamic.other$nw

# mean deg dist 
plot(summary(n ~ nodefactor(~ageM)), type="l", main="Males")
lines(mo, pch=19, col="blue")
legend("topright", legend = c("Empirical", "Model"), col=c("blue", "black"), lwd=1)

plot(summary(n ~ nodefactor(~ageF)), type="l", main="Females")
lines(fo, col="blue")
legend("topright", legend = c("Empirical", "Model"), col=c("blue", "black"), lwd=1)

# age/sex mixing
aF <- n %v% "ageF"
aM <- n %v% "ageM" 

el <- as.edgelist(n)
fem1 <- aF[el[,1]]
fem2 <- aF[el[,2]]
male1 <- aM[el[,1]]
male2 <- aM[el[,2]]

allFs <- NULL
allMs <- NULL 

for (i in 1:length(fem1)){
  if (fem1[i] != 0) {allFs[i] <- fem1[i]} 
  else {allFs[i] <- fem2[i]}
  
  if (male1[i] != 0) {allMs[i] <- male1[i]} 
  else {allMs[i] <- male2[i]}
  }

agesel <- as.data.frame(cbind(allFs, allMs))
sqrtages <- sqrt(agesel)
sqrtages$diff <- sqrtages[,1] - sqrtages[,2]
mean(sqrtages$diff)
```

```{r fullnetest }
netests <- list(marriage.netest, cohab.netest, other.netest)
saveRDS(netests, here("fits", "netests.rds"))
```