---
title: "Network Fitting"
author: "Emily Pollock"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
    html_document:
        toc: true
        toc_depth: 3
        toc_float: true
        number_sections: true
        code_folding: hide
---

```{r setup, include=FALSE}
library(ergm.ego)
library(EpiModel)
library(parallel)
library(egonet)
library(here)
source("~/Documents/Dissertation/R/Duration/Functions/finalEgodataPrep.R") # generates the egodata objects
source("~/Documents/Dissertation/R/Duration/Functions/reldur_params.R") # object with params of interest 
```

# Session Info
```{r}
sessioninfo::package_info()
```

# General Controls  

__need to update duration targets w/ estimated means from parametric model__  
__but then will also need to use CKs correction in-simiulation find undelrying relationship length in presense of mortality__  
```{r}
np <- detectCores()
# Set parallel.type
if (np==0) ptype=NULL else ptype='PSOCK'

dat <- reldur_params()
ppopsize <- dat$ppopsize
MCMCinterval <- dat$mcmcInterval
MCMCburnin <- dat$mcmcBurnin

time.step <- dat$time.step
age.width <- dat$age.width
dissolution <- dat$dissolution
#mRate <- dat$mRate

duration.marcoh <- dat$duration.marcoh
duration.other <- dat$duration.other

DissolutionMarcoh <- dissolution_coefs(dissolution=dissolution, 
                                       duration=duration.marcoh)

DissolutionOther <- dissolution_coefs(dissolution=dissolution, 
                                      duration=duration.other)
```

# Some Adjustments  
* make age/sex attribute (i.e. 15F, 23M)  
* sample down to 10,000  

```{r}
egos <- egodat_marcoh$egos

egos$ageF <- ifelse(egos$male==0, egos$age, 0)
egos$ageM <- ifelse(egos$male==1, egos$age, 0)

egodat_marcoh$alters$ageF <- ifelse(egodat_marcoh$alters$male==0, egodat_marcoh$alters$age, 0)
egodat_marcoh$alters$ageM <- ifelse(egodat_marcoh$alters$male==1, egodat_marcoh$alters$age, 0)

egodat_other$alters$ageF <- ifelse(egodat_other$alters$male==0, egodat_other$alters$age, 0)
egodat_other$alters$ageM <- ifelse(egodat_other$alters$male==1, egodat_other$alters$age, 0)

egodat_marcoh$egos <- egos
egodat_other$egos <- egos

sample_marcoh <- sample(egodat_marcoh, 10000)
sample_casual <- sample(egodat_other, 10000)

# grab binary deg dist for plots below, x2 for scaline to 20000 nodes
m <- with(sample_marcoh$egos[sample_marcoh$egos$male==1,], table(age, deg.marcoh.binary))
m <- m[,2]*2
f <- with(sample_marcoh$egos[sample_marcoh$egos$male==0,], table(age, deg.marcoh.binary))
f <- f[,2]*2

m2 <- with(sample_casual$egos[sample_casual$egos$male==1,], table(age, deg.other))
m2 <- m2[,2]*2
f2 <- with(sample_casual$egos[sample_casual$egos$male==0,], table(age, deg.other))
f2 <- f2[,2]*2
```

# Marriage/Cohab Network {.tabset .tabset-pills .tabset-fade}

## Ergm.Ego Estimation & Setup

```{r, eval=F}
fit.marcoh <- ergm.ego(sample_marcoh ~ edges + 
                         nodecov(~ageF) + 
                         nodecov(~ageF^2) +
                         nodecov(~ageM) + 
                         nodecov(~ageM^2) +
                         nodefactor(~ageF, levels=2:6) + 
                         nodefactor(~ageM, levels=2:6) + 
                         absdiff(~sqrtage + 0.1511228*(male==0)) + 
                         nodefactor("deg.other.binary") +
                         offset(nodematch("male", diff = FALSE)) +
                         #offset(nodefactor("debuted", levels=1)) + 
                         offset("concurrent"), 
                         offset.coef = c(-Inf, -Inf), #offset.coef = c(-Inf, -Inf, -Inf),
                         control = 
                         control.ergm.ego(ppop.wt = "sample", ppopsize = 20000, 
                                          ergm.control = 
                                            control.ergm(MCMLE.maxit = 200,
                                                         MCMC.interval = MCMCinterval, 
                                                         MCMC.burnin = MCMCburnin,
                                                         parallel = np,
                                                         parallel.type = ptype)))

saveRDS(fit.marcoh, here("fits", "fit.marcoh.rds"))

mpop <- environment(fit.marcoh$ergm.formula)$popnw
```

```{r}
fit.marcoh <- readRDS(here("fits", "fit.marcoh.rds"))
marcoh.netest <- ego.netest(fit.marcoh, DissolutionMarcoh)
summary(fit.marcoh)
```

## MCMC Diagnostics / GOF
```{r, warning=F, message=F, comment = F, results='hide', fig.keep='all'}
mcmc.diagnostics(fit.marcoh)
```

```{r, eval=F}
gof <- gof(fit.marcoh, GOF = "model")
saveRDS(gof, here("fits", "gof.m.rds"))
```

```{r}
gof <- readRDS(here("fits", "gof.m.rds"))
plot(gof)
```

## Static Diagnostics 

```{r, eval=F}
static.marcoh <- netdx(marcoh.netest, nsims = 500, dynamic = FALSE)
saveRDS(static.marcoh, here("fits", "static.m.rds"))
```

```{r}
static.marcoh <- readRDS(here("fits", "static.m.rds"))
static.marcoh
plot(static.marcoh)
```

## Dynamic Diagnostics 
```{r, eval=F}
dynamic.marcoh <- netdx(marcoh.netest, nsims = 5, nsteps = 1000, ncores = np, 
                       set.control.ergm = control.simulate.ergm(MCMC.burnin=1e5, 
                                                                MCMC.interval=1e5),
                       set.control.stergm = control.simulate.network(MCMC.burnin.min=1e5,
                                                                     MCMC.burnin.max=1e5))
saveRDS(dynamic.marcoh, here("fits", "dynamic.m.rds"))
```

```{r}
dynamic.marcoh <- readRDS(here("fits", "dynamic.m.rds"))
dynamic.marcoh
plot(dynamic.marcoh)
plot(dynamic.marcoh, type = "duration")
plot(dynamic.marcoh, type = "dissolution")
```


## Checking Mean Deg Dist by Age/Sex and Age/Sex Mixing are close to data 
```{r diag-diagnostic-marcoh}
n <- dynamic.marcoh$nw

plot(summary(n ~ nodefactor(~ageM)), type="l", main="Males")
lines(m, pch=19, col="blue")
legend("topright", legend = c("Empirical", "Model"), col=c("blue", "black"), lwd=1)

plot(summary(n ~ nodefactor(~ageF)), type="l", main="Females")
lines(f, col="blue")
legend("topright", legend = c("Empirical", "Model"), col=c("blue", "black"), lwd=1)

# age/sex mixing
aF <- n %v% "ageF"
aM <- n %v% "ageM" 

el <- as.edgelist(n)
fem1 <- aF[el[,1]]
fem2 <- aF[el[,2]]
male1 <- aM[el[,1]]
male2 <- aM[el[,2]]

allFs <- NULL
allMs <- NULL 

for (i in 1:length(fem1)){
  if (fem1[i] != 0) {allFs[i] <- fem1[i]} 
  else {allFs[i] <- fem2[i]}
  
  if (male1[i] != 0) {allMs[i] <- male1[i]} 
  else {allMs[i] <- male2[i]}
  }

agesel <- as.data.frame(cbind(allFs, allMs))
sqrtages <- sqrt(agesel)
sqrtages$diff <- sqrtages[,1] - sqrtages[,2]
mean(sqrtages$diff)
```


# Other Network {.tabset .tabset-pills .tabset-fade}

## Fit
```{r, eval=F} 
x <- control.ergm.ego(ppopsize = 1, ppop.wt = "sample",
                      ergm.control = control.ergm(MCMLE.maxit = 200,
                                                  MCMC.interval = MCMCinterval,
                                                  MCMC.burnin = MCMCburnin))

x$ppopsize <- mpop

fit.other <- ergm.ego(sample_casual ~ edges + 
                         nodecov(~ageF) + 
                         nodecov(~ageF^2) +
                         nodecov(~ageM) + 
                         nodecov(~ageM^2) +
                         nodefactor(~ageF, levels=2:6) + 
                         nodefactor(~ageM, levels=2:6) + 
                        absdiff(~sqrtage + 0.14505*(male==0)) + 
                        nodefactor("deg.marcoh.binary") +
                        concurrent(by=~male) +
                        offset(nodematch("male", diff = FALSE)),
                        offset.coef = c(-Inf), 
                        control = x)


#offset(nodefactor("debuted", levels=1)),
#offset.coef = c(-Inf, -Inf),

saveRDS(fit.other, here("fits", "fit.other.rds"))
```


```{r}
fit.other <- readRDS(here("fits", "fit.other.rds"))
other.netest <- ego.netest(fit.other, DissolutionOther)
summary(fit.other)
```

## MCMC Diagnostics / GOF
```{r, warning=F, message=F, comment = F, results='hide', fig.keep='all'}
mcmc.diagnostics(fit.other)
```

```{r, eval=F}
gof.o <- gof(fit.other, GOF = "model")
saveRDS(gof.o, here("fits", "gof.o.rds"))
```

```{r}
gof.o <- readRDS(here("fits", "gof.o.rds"))
plot(gof.o)
```

## Static Diagnostic 
```{r, eval=F}
static.other <- netdx(other.netest, nsims = 500, dynamic = FALSE)
saveRDS(static.other, here("fits", "static.other.rds"))
```

```{r}
static.other <- readRDS(here("fits", "static.other.rds"))
static.other
plot(static.other)
```

## Dynamic Diagnostic

```{r, eval=F}
dynamic.other <- netdx(other.netest, nsims = 5, nsteps = 1000, ncores = np,
                       set.control.ergm = control.simulate.ergm(MCMC.burnin=1e5, 
                                                                MCMC.interval=1e5),
                       set.control.stergm = control.simulate.network(MCMC.burnin.min=1e5,
                                                                     MCMC.burnin.max=1e5))
saveRDS(dynamic.other, here("fits", "dynamic.other.rds"))
```

```{r}
dynamic.other <- readRDS(here("fits", "dynamic.other.rds"))
dynamic.other
plot(dynamic.other)
plot(dynamic.other, type = "duration")
plot(dynamic.other, type = "dissolution")
```

## Checking Mean Deg Dist by Age/Sex and Age/Sex Mixing are close to data  
```{r diag-diagnostic, out.width="70%"}
n <- dynamic.other$nw

# mean deg dist 
plot(summary(n ~ nodefactor(~ageM)), type="l", ylim=c(0, max(f2)), main="Males")
lines(m2, pch=19, col="blue")
legend("topright", legend = c("Empirical", "Model"), col=c("blue", "black"), lwd=1)

plot(summary(n ~ nodefactor(~ageF)), type="l", ylim=c(0, max(f2)), main="Females")
lines(f2, col="blue")
legend("topright", legend = c("Empirical", "Model"), col=c("blue", "black"), lwd=1)

# age/sex mixing
aF <- n %v% "ageF"
aM <- n %v% "ageM" 

el <- as.edgelist(n)
fem1 <- aF[el[,1]]
fem2 <- aF[el[,2]]
male1 <- aM[el[,1]]
male2 <- aM[el[,2]]

allFs <- NULL
allMs <- NULL 

for (i in 1:length(fem1)){
  if (fem1[i] != 0) {allFs[i] <- fem1[i]} 
  else {allFs[i] <- fem2[i]}
  
  if (male1[i] != 0) {allMs[i] <- male1[i]} 
  else {allMs[i] <- male2[i]}
  }

agesel <- as.data.frame(cbind(allFs, allMs))
sqrtages <- sqrt(agesel)
sqrtages$diff <- sqrtages[,1] - sqrtages[,2]
mean(sqrtages$diff)
```

```{r fullnetest, eval=F}
#netests <- list(marcoh.netest, other.netest)
#saveRDS(netests, here("Setup", "FinalNetworks", "objects", "full", "nodefactor", "netests_nodefactor.rds"))
```