---
title: "Sexual Behaviors"
author: "Emily Pollock"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: 
  html_document:
        toc: true
        toc_depth: 3
        toc_float: true
        number_sections: true
        code_folding: hide
---

```{r ego-prep, echo=FALSE, message=FALSE, warning=FALSE}
library(ergm.ego)
library(tidyverse)
library(reshape2)
library(srvyr)
library(plotly)
library(kableExtra)


##### import data for egodata ########
egodat <- readRDS("~/nsfg_data_cleaning/Objects/fullEgodata.rds")
egodat$egos <- egodat$egos %>%
    mutate(agerange = ifelse(age >= 15 & age < 25, 1, 
                           ifelse(age >= 25 & age < 35, 2, 
                                   ifelse(age >= 35 & age < 45, 3, NA))))
#table(egodat$egos$agecat, egodat$egos$agerange)

##### make ego data objects #########
## all actives
dat <- egodata(egos=egodat$egos, alters=egodat$altersAllActive, egoWt = egodat$egos$weight, egoIDcol = "ego")
## mar/coh
datMarcoh <- egodata(egos=egodat$egos, alters=egodat$altersMarCoh, egoWt = egodat$egos$weight, egoIDcol = "ego")
## others 
datOther <- egodata(egos=egodat$egos, alters=egodat$altersOther, egoWt = egodat$egos$weight, egoIDcol = "ego")
## one times 
datOTs <- egodata(egos=egodat$egos, alters=egodat$altersOnce, egoWt = egodat$egos$weight, egoIDcol = "ego")

# full data
#nsfg <- readRDS("~/NSFG_DATA/Full/nsfg_complete.rds")
svy <- as_survey_design(egodat$egos, weights = weight, ids = ego)

actives <- svy %>% filter(pdeg.active >0)
```

# Always/Never/Sometimes Condoms {.tabset .tabset-pills .tabset-fade}
## Casual Relationships
### Agecat
```{r ans}
svy %>% 
  mutate(cat.cond = as.factor(ifelse(p.cond==0, "Never", ifelse(p.cond==1, "Always", "Sometimes")))) %>%
  filter(deg.other >= 1) %>%
  group_by(agecat, cat.cond) %>%
  summarize(count=survey_total()) %>%
  mutate(prop = count/sum(count)) %>%
  ggplot(aes(x=agecat, y=prop, group=cat.cond, color=cat.cond)) +
  geom_point() +
  geom_line() 

svy %>% 
  mutate(cat.cond = as.factor(ifelse(p.cond==0, "Never", ifelse(p.cond==1, "Always", "Sometimes")))) %>%
  filter(deg.other >= 1) %>%
  group_by(age, cat.cond) %>%
  summarize(count=survey_total()) %>%
  mutate(prop = count/sum(count)) %>%
  ggplot(aes(x=age, y=prop, group=cat.cond, color=cat.cond)) +
  geom_point() +
  geom_line() 
```

### Agecat / Race
```{r ans2}
svy %>% 
  mutate(cat.cond = as.factor(ifelse(p.cond==0, "Never", ifelse(p.cond==1, "Always", "Sometimes")))) %>%
  filter(deg.other >= 1) %>%
  group_by(agecat, race, cat.cond) %>%
  summarize(count=survey_total()) %>%
  mutate(prop = count/sum(count)) %>%
  ggplot(aes(x=race, y=prop, group=cat.cond, color=cat.cond)) +
  geom_point() +
  geom_line() +
  facet_wrap(~agecat)
```

### "Sometimes" Range
```{r sometimes-cas}
svy %>% 
  mutate(cat.cond = as.factor(ifelse(p.cond==0, "Never", ifelse(p.cond==1, "Always", "Sometimes")))) %>%
  filter(deg.other >= 1, cat.cond=="Sometimes") %>%
  summarise(mean = survey_mean(p.cond), m=survey_quantile(p.cond, c(0.25, 0.5, 0.75))) %>%
  kable() %>%
  kable_styling()
```

## Marriage/Cohabs
### Age 
```{r ans-m}
svy %>% 
  mutate(cat.cond = as.factor(ifelse(p.cond==0, "Never", ifelse(p.cond==1, "Always", "Sometimes")))) %>%
  filter(deg.marcoh==1) %>%
  group_by(agecat, cat.cond) %>%
  summarize(count=survey_total()) %>%
  mutate(prop = count/sum(count)) %>%
  ggplot(aes(x=agecat, y=prop, group=cat.cond, color=cat.cond)) +
  geom_point() +
  geom_line()

  
svy %>% 
  mutate(cat.cond = as.factor(ifelse(p.cond==0, "Never", ifelse(p.cond==1, "Always", "Sometimes")))) %>%
  filter(deg.marcoh==1) %>%
  group_by(age, cat.cond) %>%
  summarize(count=survey_total()) %>%
  mutate(prop = count/sum(count)) %>%
  ggplot(aes(x=age, y=prop, group=cat.cond, color=cat.cond)) +
  geom_point() +
  geom_line()


t <- svy %>% 
  mutate(cat.cond = as.factor(ifelse(p.cond==0, "Never", ifelse(p.cond==1, "Always", "Sometimes")))) %>%
  filter(deg.marcoh==1) %>%
  group_by(agecat, cat.cond) %>%
  summarize(count=survey_total()) %>%
  filter(cat.cond=="Always")
```

### Agecat / Race
```{r ans2-m}
svy %>% 
  mutate(cat.cond = as.factor(ifelse(p.cond==0, "Never", ifelse(p.cond==1, "Always", "Sometimes")))) %>%
  filter(deg.marcoh==1) %>%
  group_by(agecat, race, cat.cond) %>%
  summarize(count=survey_total()) %>%
  group_by(agecat, race) %>%
  mutate(prop = count/sum(count)) %>%
  ggplot(aes(x=race, y=prop, group=cat.cond, color=cat.cond)) +
  geom_point() +
  geom_line() +
  facet_wrap(~agecat)
```

### "Sometimes" Range
```{r sometimes-mar}
svy %>% 
  mutate(cat.cond = as.factor(ifelse(p.cond==0, "Never", ifelse(p.cond==1, "Always", "Sometimes")))) %>%
  filter(deg.marcoh== 1, cat.cond=="Sometimes") %>%
  summarise(mean = survey_mean(p.cond), m=survey_quantile(p.cond, c(0.25, 0.5, 0.75))) %>%
  kable() %>%
  kable_styling()
```

# Sex Acts Per Week {.tabset .tabset-pills .tabset-fade}
## Casual
### Age  
```{r cas-acts-age}
meansex <- svy %>% 
  filter(deg.other >=1, sex4wk<998) %>% 
  summarize(mean = survey_mean(sex4wk/4, vartype="ci")) 
  
svy %>% 
  filter(deg.other >= 1, sex4wk<998) %>%
  group_by(agecat) %>%
  summarize(mean = survey_mean(sex4wk/4, vartype="ci")) %>%
  ggplot(aes(x=agecat, y=mean, color=agecat)) +
  geom_point() + 
  geom_errorbar(aes(ymin=mean_low, ymax=mean_upp), width=.2,
                 position=position_dodge(.9)) +
  ggtitle("Sex Acts Per Week by Agecat") 

  
svy %>% 
  filter(deg.other >= 1, sex4wk<998) %>%
  group_by(age) %>%
  summarize(mean = survey_mean(sex4wk/4, vartype="ci")) %>%
  ggplot(aes(x=age, y=mean, color=age)) +
  geom_point() + 
  geom_errorbar(aes(ymin=mean_low, ymax=mean_upp), width=.2,
                 position=position_dodge(.9)) +
  ggtitle("Sex Acts Per Week by Age") 
```


### Age / Race  
```{r cas-acts-race}
svy %>% 
  filter(deg.other >= 1, sex4wk<998) %>%
  group_by(race, agecat) %>%
  summarize(mean = survey_mean(sex4wk/4, vartype="ci")) %>%
  ggplot(aes(x=race, y=mean, color=race)) +
  geom_point() + 
  geom_errorbar(aes(ymin=mean_low, ymax=mean_upp), width=.2,
                 position=position_dodge(.9)) +
  facet_wrap(~agecat) +
  ggtitle("Sex Acts Per Week by Agecat/Race") 
```

## Marriage/Cohab
### Age 
```{r mar-acts}
meansex <- svy %>% 
  filter(deg.marcoh==1, sex4wk<998) %>% 
  summarize(mean = survey_mean(sex4wk/4, vartype="ci"))
  
svy %>% 
  filter(deg.marcoh == 1, sex4wk<998) %>%
  group_by(agecat) %>%
  summarize(mean = survey_mean(sex4wk/4, vartype="ci")) %>%
  ggplot(aes(x=agecat, y=mean, color=agecat)) +
  geom_point() + 
  geom_errorbar(aes(ymin=mean_low, ymax=mean_upp), width=.2,
                 position=position_dodge(.9)) +
  ggtitle("Sex Acts Per Week by Agecat") 

svy %>% 
  filter(deg.marcoh == 1, sex4wk<998) %>%
  group_by(age) %>%
  summarize(mean = survey_mean(sex4wk/4, vartype="ci")) %>%
  ggplot(aes(x=age, y=mean, color=age)) +
  geom_point() + 
  geom_errorbar(aes(ymin=mean_low, ymax=mean_upp), width=.2,
                 position=position_dodge(.9)) +
  ggtitle("Sex Acts Per Week by Age") 
```

### Age / Race 
```{r mar-acts-race}
svy %>% 
  filter(deg.other >= 1, sex4wk<998) %>%
  group_by(race, agecat) %>%
  summarize(mean = survey_mean(sex4wk/4, vartype="ci")) %>%
  ggplot(aes(x=race, y=mean, color=race)) +
  geom_point() + 
  geom_errorbar(aes(ymin=mean_low, ymax=mean_upp), width=.2,
                 position=position_dodge(.9)) +
  facet_wrap(~agecat) +
  ggtitle("Sex Acts Per Week by Agecat/Race") +
  ylim(0,3)
```

# old - By Age Range (Condensed Age Categories)  
1 = 15-24 year olds  
2 = 25-34 year olds  
3 = 35-44 year olds  

## Degree Dist {.tabset .tabset-pills .tabset-fade}  

this is using the egodata used in ch 1 for demography sims - but I should probably either add back in the over-45 alters for the "typical" 35-44 year old experience? or remove older alters for lower ages too (i.e. over 25 years old in youngest...)  

```{r deg-agerange}
degs <- svy %>% 
        mutate(sex=as.factor(sex), deg.marcoh=as.factor(deg.marcoh), deg.other=as.factor(deg.other), agerange=as.factor(agerange)) %>%
        group_by(agerange, sex, deg.marcoh, deg.other, .drop = FALSE) %>% 
        summarize(n = survey_total()) %>% 
        group_by(agerange, sex) %>%
        mutate(prop = n/sum(n)) %>%
        select(-n, -n_se) %>%
        pivot_wider(names_from = deg.other, values_from=prop) 

degs <- degs[,-c(1:2)]
degs[,2:5] <- round(degs[,2:5],3)

degs %>%
  kable() %>%
  kable_styling("striped") %>%
  pack_rows("Age Range 1", 1, 4) %>%
  pack_rows("Females", 1, 2) %>%
  pack_rows("Males", 3, 4) %>%
  pack_rows("Age Range 2", 5, 8) %>%
  pack_rows("Age Range 3", 9, 12) %>%
  pack_rows("Females", 5, 6) %>%
  pack_rows("Males", 7, 8) %>%
  pack_rows("Females", 9, 10) %>%
  pack_rows("Males", 11, 12) %>%
  add_header_above(c(" "=1, "Deg Casual"=4))

```

## Condoms: Proportion Always/Never/Sometimes {.tabset .tabset-pills .tabset-fade}
### Casual
```{r cascondoms-agerange}
cas.condoms <- svy %>% 
  mutate(cat.cond = as.factor(ifelse(p.cond==0, "Never", ifelse(p.cond==1, "Always", "Sometimes")))) %>%
  filter(deg.other >= 1) %>%
  group_by(agerange, cat.cond) %>%
  summarize(count=survey_total()) %>%
  mutate(prop = count/sum(count)) %>%
  ggplot(aes(x=cat.cond, y=prop, fill=cat.cond)) +
  geom_col() +
  facet_wrap(~agerange)

ggplotly(cas.condoms)

svy %>% 
  mutate(cat.cond = as.factor(ifelse(p.cond==0, "Never", ifelse(p.cond==1, "Always", "Sometimes")))) %>%
  filter(deg.other >= 1, cat.cond=="Sometimes") %>%
  group_by(agerange) %>%
  summarise(mean = round(survey_mean(p.cond),2), m=round(survey_quantile(p.cond, c(0.25, 0.5, 0.75)), 3)) %>%
  kable(caption="Distribution of Sometimes Condoms") %>%
  kable_styling()
```
### Marriage/Cohab  
```{r marcondoms-agerange}
mar.condoms <- svy %>% 
  mutate(cat.cond = as.factor(ifelse(p.cond==0, "Never", ifelse(p.cond==1, "Always", "Sometimes")))) %>%
  filter(deg.marcoh >= 1) %>%
  group_by(agerange, cat.cond) %>%
  summarize(count=survey_total()) %>%
  mutate(prop = count/sum(count)) %>%
  ggplot(aes(x=cat.cond, y=prop, fill=cat.cond)) +
  geom_col() +
  facet_wrap(~agerange)

ggplotly(mar.condoms)

svy %>% 
  mutate(cat.cond = as.factor(ifelse(p.cond==0, "Never", ifelse(p.cond==1, "Always", "Sometimes")))) %>%
  filter(deg.marcoh == 1, cat.cond=="Sometimes") %>%
  group_by(agerange) %>%
  summarise(mean = round(survey_mean(p.cond),2), m=round(survey_quantile(p.cond, c(0.25, 0.5, 0.75)), 3)) %>%
  kable(caption="Distribution of Sometimes Condoms") %>%
  kable_styling()
```

## Sex Acts Per Week {.tabset .tabset-pills .tabset-fade}   
### Casual  
```{r acts-agerange-casual}
cas.acts <- svy %>% 
  filter(deg.other >= 1, sex4wk<998) %>%
  mutate(agerange = as.factor(agerange)) %>%
  group_by(agerange) %>%
  summarize(mean = survey_mean(sex4wk/4, vartype="ci")) %>%
  ggplot(aes(x=agerange, y=mean, color=agerange)) +
  geom_point() + 
  geom_errorbar(aes(ymin=mean_low, ymax=mean_upp), width=.2,
                 position=position_dodge(.9)) +
  ggtitle("Sex Acts Per Week by Age Range") 

ggplotly(cas.acts)
```

### Marriage/Cohab  
```{r acts-agerange-marcoh}
mar.acts <- svy %>% 
  filter(deg.marcoh == 1, sex4wk<998) %>%
  mutate(agerange = as.factor(agerange)) %>%
  group_by(agerange) %>%
  summarize(mean = survey_mean(sex4wk/4, vartype="ci")) %>%
  ggplot(aes(x=agerange, y=mean, color=agerange)) +
  geom_point() + 
  geom_errorbar(aes(ymin=mean_low, ymax=mean_upp), width=.2,
                 position=position_dodge(.9)) +
  ggtitle("Sex Acts Per Week by Age Range") 

ggplotly(mar.acts)
```

# old - Proportion of Sex Acts w/ Condom in Last Week 

## Causal Relationships {.tabset .tabset-pills .tabset-fade}
### Age  
```{r conds_cas_age, message=FALSE, warning=FALSE}
cas.agecat.med <- svy %>% 
  filter(deg.other >= 1) %>% 
  group_by(agecat) %>%
  summarize(med = survey_median(p.cond, vartype=NULL))

cas.agecat <- svy %>% 
  filter(deg.other >= 1) %>% 
  group_by(agecat) %>%
  summarize(mean = survey_mean(p.cond, vartype="ci")) %>%
  ggplot(aes(x=agecat, y=mean)) +
    geom_point() +
    geom_line() +
    geom_errorbar(aes(ymin=mean_low, ymax=mean_upp), width=.2,
                 position=position_dodge(.9))+
  geom_point(data=cas.agecat.med, aes(y=med), color="blue")
  
ggplotly(cas.agecat)
```


### Race  
```{r condomsracecas, message=FALSE, warning=FALSE}
cas.race.med <- svy %>% 
  filter(deg.other >= 1) %>% 
  group_by(race) %>%
  summarize(med = survey_median(p.cond, vartype=NULL))

cas.race <- svy %>% 
  filter(deg.other >= 1) %>% 
  group_by(race) %>%
  summarize(mean = survey_mean(p.cond, vartype="ci")) %>%
  ggplot(aes(x=race, y=mean)) +
    geom_point() +
    geom_errorbar(aes(ymin=mean_low, ymax=mean_upp), width=.2,
                 position=position_dodge(.9))+
  geom_point(data=cas.race.med, aes(y=med), color="blue")
  
ggplotly(cas.race)
```


### Activity Level  
```{r, message=FALSE, warning=FALSE}
cas.deg.med <- svy %>% 
  filter(deg.other >= 1) %>% 
  group_by(deg.other) %>%
  summarize(med = survey_median(p.cond, vartype=NULL))

cas.deg <- svy %>% 
  filter(deg.other >= 1) %>% 
  group_by(deg.other) %>%
  summarize(mean = survey_mean(p.cond, vartype="ci")) %>%
  ggplot(aes(x=deg.other, y=mean)) +
    geom_point() +
    geom_errorbar(aes(ymin=mean_low, ymax=mean_upp), width=.2,
                 position=position_dodge(.9))+
  geom_point(data=cas.deg.med, aes(y=med), color="blue")
  
ggplotly(cas.deg)

```

### Joint  
```{r condsjoint, message=FALSE, warning=FALSE}
cas.joint <- svy %>% 
  filter(deg.other >= 1) %>% 
  mutate(deg.other=as.factor(deg.other)) %>%
  group_by(deg.other, agecat, race) %>%
  summarize(mean = survey_mean(p.cond, vartype=NULL)) %>%
  ggplot(aes(x=agecat, y=mean, group=deg.other, color=deg.other)) +
    geom_point() +
  facet_wrap(~race)
  
ggplotly(cas.joint)

```

## Marriage/Cohabs {.tabset .tabset-pills .tabset-fade}
### Age  
```{r conds_mar_age, message=FALSE, warning=FALSE}
mar.agecat.med <- svy %>% 
  filter(deg.marcoh >= 1) %>% 
  group_by(agecat) %>%
  summarize(med = survey_median(p.cond, vartype=NULL))

mar.agecat <- svy %>% 
  filter(deg.marcoh >= 1) %>% 
  group_by(agecat) %>%
  summarize(mean = survey_mean(p.cond, vartype="ci")) %>%
  ggplot(aes(x=agecat, y=mean)) +
    geom_point() +
    geom_line() +
    geom_errorbar(aes(ymin=mean_low, ymax=mean_upp), width=.2,
                 position=position_dodge(.9))+
  geom_point(data=mar.agecat.med, aes(y=med), color="blue")
  
ggplotly(mar.agecat)
```


### Race  
```{r condomsrace, message=FALSE, warning=FALSE}
mar.race.med <- svy %>% 
  filter(deg.marcoh >= 1) %>% 
  group_by(race) %>%
  summarize(med = survey_median(p.cond, vartype=NULL))

mar.race <- svy %>% 
  filter(deg.marcoh >= 1) %>% 
  group_by(race) %>%
  summarize(mean = survey_mean(p.cond, vartype="ci")) %>%
  ggplot(aes(x=race, y=mean)) +
    geom_point() +
    geom_errorbar(aes(ymin=mean_low, ymax=mean_upp), width=.2,
                 position=position_dodge(.9))+
  geom_point(data=mar.race.med, aes(y=med), color="blue")
  
ggplotly(mar.race)
```
