---
title: "EPT Results"
author: "Emily Pollock"
date: "4/15/2021"
output: 
  html_document:
        toc: true
        toc_depth: 3
        toc_float: true
        number_sections: true
        code_folding: hide
---

```{r s, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
library(here)
library(kableExtra)
library(tidyverse)
source(here("functions", "analyze_sims.R"))

s01 <- readRDS(here("sims", "may2", "simBase0.rds"))
s02 <- readRDS(here("sims", "may2", "simAvg0.rds"))
s03 <- readRDS(here("sims", "may2", "simNc0.rds"))

s1 <- readRDS(here("sims", "may2", "simBase.rds"))
s2 <- readRDS(here("sims", "may2", "simAvg.rds"))
s3 <- readRDS(here("sims", "may2", "simNc.rds"))

s1ept <- readRDS(here("sims", "may2", "simBaseEPT.rds"))
s2ept <- readRDS(here("sims", "may2", "simAvgEPT.rds"))
s3ept <- readRDS(here("sims", "may2", "simNcEPT.rds"))

s1epthigh <- readRDS(here("sims", "may2", "simBaseEPThigh.rds"))
s2epthigh <- readRDS(here("sims", "may2", "simAvgEPThigh.rds"))
s3epthigh <- readRDS(here("sims", "may2", "simNcEPThigh.rds"))

s1ept100 <- readRDS(here("sims", "may2", "simBaseEPT100.rds"))
s2ept100 <- readRDS(here("sims", "may2", "simAvgEPT100.rds"))
s3ept100 <- readRDS(here("sims", "may2", "simNcEPT100.rds"))

dat0 <- analyze_sim(s01, start = 2000)
dat02 <- analyze_sim(s02, start = 2000)
dat03 <- analyze_sim(s03, start = 2000)

dat <- analyze_sim(s1, start = 2000)
dat2 <- analyze_sim(s2, start = 2000)
dat3 <- analyze_sim(s3, start = 2000)

datept <- analyze_sim(s1ept, start = 2000)
dat2ept <- analyze_sim(s2ept, start = 2000)
dat3ept <- analyze_sim(s3ept, start = 2000)

datepthigh <- analyze_sim(s1epthigh, start = 2000)
dat2epthigh <- analyze_sim(s2epthigh, start = 2000)
dat3epthigh <- analyze_sim(s3epthigh, start = 2000)

datept1 <- analyze_sim(s1ept100, start = 2000)
dat2ept1 <- analyze_sim(s2ept100, start = 2000)
dat3ept1 <- analyze_sim(s3ept100, start = 2000)
```

# Overview 

 - Five EPT Scenarios by index patient acceptance : 0, 25, 50, 75, All Ongoing Partnerships
 - Three Concurrency Scenarios: By Sex (higher male concurrency), Average, and No concurrency
 - Each scenario run for 5 simulations for 80 years, analysis uses last ~40 years where epidemics are at equilibrium  


# Prevalence {.tabset}
## Plot
```{r prev}
library(tidyverse)
femaleprev <- rbind(dat0[[1]][[1]], dat[[1]][[1]], datept[[1]][[1]], datepthigh[[1]][[1]], datept1[[1]][[1]], 
                    dat02[[1]][[1]], dat2[[1]][[1]], dat2ept[[1]][[1]], dat2epthigh[[1]][[1]], dat2ept1[[1]][[1]], 
                    dat03[[1]][[1]], dat3[[1]][[1]], dat2ept[[1]][[1]], dat3epthigh[[1]][[1]], dat3ept1[[1]][[1]])

femaleprev$Behavior <- factor(c(rep("M.F.Concurrency", 5), rep("Avg.Concurrency", 5), rep("No.Concurrency", 5)), levels=c("M.F.Concurrency", "Avg.Concurrency", "No.Concurrency"))

femaleprev$Treatment = factor(rep(c("No Partner Treatment", "Low Partner Treatment", "Medium Partner Treatment", "High Partner Treatment", "All Ongoing Partners"),3), levels = c("No Partner Treatment", "Low Partner Treatment", "Medium Partner Treatment", "High Partner Treatment", "All Ongoing Partners"))

maleprev <- rbind(dat0[[1]][[2]], dat[[1]][[2]], datept[[1]][[2]], datepthigh[[1]][[2]], datept1[[1]][[2]], 
                    dat02[[1]][[2]], dat2[[1]][[2]], dat2ept[[1]][[2]], dat2epthigh[[1]][[2]], dat2ept1[[1]][[2]], 
                    dat03[[1]][[2]], dat3[[1]][[2]], dat2ept[[1]][[2]], dat3epthigh[[1]][[2]], dat3ept1[[1]][[2]])

maleprev$Behavior <- factor(c(rep("M.F.Concurrency", 5), rep("Avg.Concurrency", 5), rep("No.Concurrency", 5)), levels=c("M.F.Concurrency", "Avg.Concurrency", "No.Concurrency"))

maleprev$Treatment = factor(rep(c("No Partner Treatment", "Low Partner Treatment", "Medium Partner Treatment", "High Partner Treatment", "All Ongoing Partners"),3), levels = c("No Partner Treatment", "Low Partner Treatment", "Medium Partner Treatment", "High Partner Treatment", "All Ongoing Partners"))

simprev <- rbind(femaleprev, maleprev)
simprev$Sex <- c(rep("Female", 15), rep("Male", 15))

simprev %>% ggplot(aes(x=Treatment, y=mean, col=Sex)) +
  geom_point(size=3) +
  geom_line(aes(x=Treatment, y=mean, group=Sex)) +
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1) +
  facet_wrap(~Behavior) +
  theme(axis.text.x = element_text(angle = 45)) +
  ylim(0,0.05)
```

## Table 
(low/high is mean +/- 2*SE)  
```{r prev-tab}
kable(simprev) %>%
  kable_styling()
```

# Incidence 
## Overall by Sex 
```{r incid-avg}
i.fem.s01 <- dat0[[2]][[1]]
i.fem.s01 <- apply(i.fem.s01, 2, mean)
i.male.s01 <- dat0[[2]][[2]]
i.male.s01 <- apply(i.male.s01, 2, mean)

i.fem.s02 <- dat02[[2]][[1]]
i.fem.s02 <- apply(i.fem.s02, 2, mean)
i.male.s02 <- dat02[[2]][[2]]
i.male.s02 <- apply(i.male.s02, 2, mean)

i.fem.s03 <- dat03[[2]][[1]]
i.fem.s03 <- apply(i.fem.s03, 2, mean)
i.male.s03 <- dat03[[2]][[2]]
i.male.s03 <- apply(i.male.s03, 2, mean)

i.fem.s1 <- apply(dat[[2]][[1]], 2, mean)
i.male.s1 <- apply(dat[[2]][[2]], 2, mean)
i.fem.s2 <- apply(dat2[[2]][[1]], 2, mean)
i.male.s2 <- apply(dat2[[2]][[2]], 2, mean)
i.fem.s3 <- apply(dat3[[2]][[1]], 2, mean)
i.male.s3 <- apply(dat3[[2]][[2]], 2, mean)

i.fem.s1ept <- apply(datept[[2]][[1]], 2, mean)
i.male.s1ept <- apply(datept[[2]][[2]], 2, mean)
i.fem.s2ept <- apply(dat2ept[[2]][[1]], 2, mean)
i.male.s2ept <- apply(dat2ept[[2]][[2]], 2, mean)
i.fem.s3ept <- apply(dat3ept[[2]][[1]], 2, mean)
i.male.s3ept <- apply(dat3ept[[2]][[2]], 2, mean)

i.fem.s1epthigh <- apply(datepthigh[[2]][[1]], 2, mean)
i.male.s1epthigh <- apply(datepthigh[[2]][[2]], 2, mean)
i.fem.s2epthigh <- apply(dat2epthigh[[2]][[1]], 2, mean)
i.male.s2epthigh <- apply(dat2epthigh[[2]][[2]], 2, mean)
i.fem.s3epthigh <- apply(dat3epthigh[[2]][[1]], 2, mean)
i.male.s3epthigh <- apply(dat3epthigh[[2]][[2]], 2, mean)

i.fem.s1ept1 <- apply(datept1[[2]][[1]], 2, mean)
i.male.s1ept1 <-apply(datept1[[2]][[2]], 2, mean)
i.fem.s2ept1 <- apply(dat2ept1[[2]][[1]], 2, mean)
i.male.s2ept1 <- apply(dat2ept1[[2]][[2]], 2, mean)
i.fem.s3ept1 <- apply(dat3ept1[[2]][[1]], 2, mean)
i.male.s3ept1 <- apply(dat3ept1[[2]][[2]], 2, mean)

fems <- rbind(i.fem.s01, i.fem.s02, i.fem.s03, 
              i.fem.s1, i.fem.s2, i.fem.s3,
              i.fem.s1ept, i.fem.s2ept, i.fem.s3ept,
              i.fem.s1epthigh, i.fem.s2epthigh, i.fem.s3epthigh,
              i.fem.s1ept1, i.fem.s2ept1, i.fem.s3ept1)

males <- rbind(i.male.s01, i.male.s02, i.male.s03,
              i.male.s1, i.male.s2, i.male.s3,
              i.male.s1ept, i.male.s2ept, i.male.s3ept,
              i.male.s1epthigh, i.male.s2epthigh, i.male.s3epthigh,
              i.male.s1ept1, i.male.s2ept1, i.male.s3ept1)

incid <- as.data.frame(rbind(fems, males))
incid$Sex <- c(rep("Females", 15), rep("Males", 15))
incid$Behavior <- factor(rep(c("M.F.Concurrency","Avg.Concurrency", "No.Concurrency"),5), levels=c("M.F.Concurrency", "Avg.Concurrency", "No.Concurrency"))
incid$Treatment <- factor(c(rep("No Partner Treatment", 3), rep("Low Partner Treatment", 3), rep("Medium Partner Treatment", 3), rep("High Partner Treatment", 3), rep("All Ongoing Partners", 3)), levels = c("No Partner Treatment", "Low Partner Treatment", "Medium Partner Treatment", "High Partner Treatment", "All Ongoing Partners"))

incid %>% ggplot(aes(x=Treatment, y=mean, col=Sex)) +
  geom_point(size=2) +
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1)+
  facet_wrap(~Behavior) +
  ylab("Mean Incidence Rate") +
  theme(axis.text.x = element_text(angle=45))

incid %>% ggplot(aes(x=Behavior, y=mean, col=Sex)) +
  geom_point(size=2) +
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1)+
  facet_wrap(~Treatment, nrow=1) +
  theme(axis.text.x = element_text(angle=45)) +
  ylab("Mean Incidence Rate")
```

## Females by AgeCat{.tabset}
### Plot
```{r incid-female}
i.fem.s01 <- dat0[[2]][[1]]
i.male.s01 <- dat0[[2]][[2]]
i.fem.s02 <- dat02[[2]][[1]]
i.male.s02 <- dat02[[2]][[2]]
i.fem.s03 <- dat03[[2]][[1]]
i.male.s03 <- dat03[[2]][[2]]

i.fem.s1 <- dat[[2]][[1]]
i.male.s1 <- dat[[2]][[2]]
i.fem.s2 <- dat2[[2]][[1]]
i.male.s2 <- dat2[[2]][[2]]
i.fem.s3 <- dat3[[2]][[1]]
i.male.s3 <- dat3[[2]][[2]]

i.fem.s1ept <- datept[[2]][[1]]
i.male.s1ept <- datept[[2]][[2]]
i.fem.s2ept <- dat2ept[[2]][[1]]
i.male.s2ept <- dat2ept[[2]][[2]]
i.fem.s3ept <- dat3ept[[2]][[1]]
i.male.s3ept <- dat3ept[[2]][[2]]

i.fem.s1epthigh <- datepthigh[[2]][[1]]
i.male.s1epthigh <- datepthigh[[2]][[2]]
i.fem.s2epthigh <- dat2epthigh[[2]][[1]]
i.male.s2epthigh <- dat2epthigh[[2]][[2]]
i.fem.s3epthigh <- dat3epthigh[[2]][[1]]
i.male.s3epthigh <- dat3epthigh[[2]][[2]]

i.fem.s1ept1 <- datept1[[2]][[1]]
i.male.s1ept1 <- datept1[[2]][[2]]
i.fem.s2ept1 <- dat2ept1[[2]][[1]]
i.male.s2ept1 <- dat2ept1[[2]][[2]]
i.fem.s3ept1 <- dat3ept1[[2]][[1]]
i.male.s3ept1 <- dat3ept1[[2]][[2]]

fems <- rbind(i.fem.s01, i.fem.s02, i.fem.s03, 
              i.fem.s1, i.fem.s2, i.fem.s3,
              i.fem.s1ept, i.fem.s2ept, i.fem.s3ept,
              i.fem.s1epthigh, i.fem.s2epthigh, i.fem.s3epthigh,
              i.fem.s1ept1, i.fem.s2ept1, i.fem.s3ept1)

fems$Behavior <- factor(rep(c(rep("M.F.Concurrency", 6), rep("Avg.Concurrency", 6), rep("No.Concurrency", 6)),5), levels=c("M.F.Concurrency", "Avg.Concurrency", "No.Concurrency"))

fems$Treatment <- factor(c(rep("No Partner Treatment", 6*3), rep("Low Partner Treatment", 6*3), rep("Medium Partner Treatment", 6*3), rep("High Partner Treatment", 6*3), rep("All Ongoing Partners", 6*3)), levels = c("No Partner Treatment", "Low Partner Treatment", "Medium Partner Treatment", "High Partner Treatment", "All Ongoing Partners"))

fems$AgeCat <- factor(rep(c("15-19", "20-24", "25-29", "30-34", "35-39", "40-44"),15))

fems %>% ggplot(aes(x=AgeCat, y=mean, col=Treatment)) +
  geom_point() +
  geom_line(aes(x=AgeCat, y=mean, group=Treatment)) + 
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1)+
  facet_wrap("Behavior")  +
  theme(axis.text.x = element_text(angle = 45))
```

### Table 
```{r incid-female-tab}
kable(fems) %>%
  kable_styling()
```

## Males {.tabset}
### Plot
```{r incid-male}
males <- rbind(i.male.s01, i.male.s02, i.male.s03,
              i.male.s1, i.male.s2, i.male.s3,
              i.male.s1ept, i.male.s2ept, i.male.s3ept,
              i.male.s1epthigh, i.male.s2epthigh, i.male.s3epthigh,
              i.male.s1ept1, i.male.s2ept1, i.male.s3ept1)

males$Behavior <- factor(rep(c(rep("M.F.Concurrency", 6), rep("Avg.Concurrency", 6), rep("No.Concurrency", 6)),5), levels=c("M.F.Concurrency", "Avg.Concurrency", "No.Concurrency"))

males$Treatment <- factor(c(rep("No Partner Treatment", 6*3), rep("Low Partner Treatment", 6*3), rep("Medium Partner Treatment", 6*3), rep("High Partner Treatment", 6*3), rep("All Ongoing Partners", 6*3)), levels = c("No Partner Treatment", "Low Partner Treatment", "Medium Partner Treatment", "High Partner Treatment", "All Ongoing Partners"))

males$AgeCat <- factor(rep(c("15-19", "20-24", "25-29", "30-34", "35-39", "40-44"),15))

males %>% ggplot(aes(x=AgeCat, y=mean, col=Treatment)) +
  geom_point() +
  geom_line(aes(x=AgeCat, y=mean, group=Treatment)) + 
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1)+
  facet_wrap("Behavior")  +
  theme(axis.text.x = element_text(angle = 45))
```

### Table 
```{r incid-male-tab}
kable(males) %>%
  kable_styling()
```

```{r prevcheck, eval=F}
library(EpiModel)
plot(s1, y=c("i.num.feml", "i.num.male"), legend=T) #2000
plot(s1ept, y=c("i.num.feml", "i.num.male"), legend=T)
plot(s1epthigh, y=c("i.num.feml", "i.num.male"), legend=T)

plot(s2, y=c("i.num.feml", "i.num.male"), legend=T)
plot(s2ept, y=c("i.num.feml", "i.num.male"), legend=T)
plot(s2epthigh, y=c("i.num.feml", "i.num.male"), legend=T)

plot(s3, y=c("i.num.feml", "i.num.male"), legend=T)
plot(s3ept, y=c("i.num.feml", "i.num.male"), legend=T)
plot(s3epthigh, y=c("i.num.feml", "i.num.male"), legend=T)
```


# Reinfection

## Females {.tabset}
### Plots
```{r reinfs-female}
r <- rbind(dat0[[3]][[1]], dat02[[3]][[1]], dat03[[3]][[1]],
          dat[[3]][[1]], dat2[[3]][[1]], dat3[[3]][[1]],
           datept[[3]][[1]], dat2ept[[3]][[1]], dat3ept[[3]][[1]],
           datepthigh[[3]][[1]], dat2epthigh[[3]][[1]], dat3epthigh[[3]][[1]],
           datept1[[3]][[1]], dat2ept1[[3]][[1]], dat3ept1[[3]][[1]])

r$Behavior <- rep(c(rep("M.F.Concurrency",6), rep( "Avg.Concurrency",6), rep( "No.Concurrency",6)),5)
r$Behavior <- factor(r$Behavior, levels=c("M.F.Concurrency", "Avg.Concurrency", "No.Concurrency"))

r$Treatment <- c(rep("No Partner Treatment", 18), rep("Low Partner Treatment", 18), rep("Medium Partner Treatment", 18), rep("High Partner Treatment", 18), rep("All Ongoing Partners", 18))

r$Treatment <- factor(r$Treatment, levels = c("No Partner Treatment", "Low Partner Treatment", "Medium Partner Treatment", "High Partner Treatment", "All Ongoing Partners"))

r$ReinfType <- rep(c(rep("Following Natural Recovery", 3), rep("Following Diagnosis and Recovery",3)),15)

r$Reinfection <- factor(rep(c("Twelve", "Six", "Three"),30), levels = c("Three", "Six", "Twelve"))


r %>% filter(Behavior== "M.F.Concurrency") %>% 
  ggplot(aes(x=Treatment, y=mean, col=Reinfection)) +
  geom_point(size=2) +
  geom_line(aes(x=Treatment, y=mean, group=Reinfection)) + 
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1) +
  facet_wrap(~ReinfType, nrow=1)  +
  theme(axis.text.x = element_text(angle = 45)) +
  ylim(0,0.6) +
  ggtitle("Higher Male Concurrency")

r %>% filter(Behavior== "Avg.Concurrency") %>% 
  ggplot(aes(x=Treatment, y=mean, col=Reinfection)) +
  geom_point(size=2) +
  geom_line(aes(x=Treatment, y=mean, group=Reinfection)) + 
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1) +
  facet_wrap(~ReinfType, nrow=1)  +
  theme(axis.text.x = element_text(angle = 45)) +
  ylim(0,0.6) +
  ggtitle("Average Concurrency")

r %>% filter(Behavior== "No.Concurrency") %>% 
  ggplot(aes(x=Treatment, y=mean, col=Reinfection)) +
  geom_point(size=2) +
  geom_line(aes(x=Treatment, y=mean, group=Reinfection)) + 
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1) +
  facet_wrap(~ReinfType, nrow=1)  +
  theme(axis.text.x = element_text(angle = 45)) +
  ylim(0,0.6) +
  ggtitle("No Concurrency")

r %>% filter(Reinfection== "Three") %>% 
  ggplot(aes(x=Behavior, y=mean, col=Treatment)) +
  geom_point(size=2) +
  #geom_line(aes(x=Behavior, y=mean, group=Treatment)) + 
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1) +
  facet_wrap(~ReinfType, nrow=1)  +
  theme(axis.text.x = element_text(angle = 45)) +
  ylim(0,0.5) +
  ggtitle("Proportion Reinfected within 3 Months of Diagnosis or Previous Infection")
```

### Table 

```{r reinf-female-tab}
kable(r) %>%
  kable_styling()
```

## Males {.tabset}
### Plots
```{r reinfs-male}
r2 <- rbind(dat0[[3]][[2]], dat02[[3]][[2]], dat03[[3]][[2]],
            dat[[3]][[2]], dat2[[3]][[2]], dat3[[3]][[2]],
           datept[[3]][[2]], dat2ept[[3]][[2]], dat3ept[[3]][[2]],
           datepthigh[[3]][[2]], dat2epthigh[[3]][[2]], dat3epthigh[[3]][[2]],
           datept1[[3]][[2]], dat2ept1[[3]][[2]], dat3ept1[[3]][[2]])

r2$Behavior <- rep(c(rep("M.F.Concurrency",6), rep( "Avg.Concurrency",6), rep( "No.Concurrency",6)),5)
r2$Behavior <- factor(r2$Behavior, levels=c("M.F.Concurrency", "Avg.Concurrency", "No.Concurrency"))

r2$Treatment <- c(rep("No Partner Treatment", 18), rep("Low Partner Treatment", 18), rep("Medium Partner Treatment", 18), rep("High Partner Treatment", 18), rep("All Ongoing Partners", 18))

r2$Treatment <- factor(r2$Treatment, levels = c("No Partner Treatment", "Low Partner Treatment", "Medium Partner Treatment", "High Partner Treatment", "All Ongoing Partners"))

r2$ReinfType <- rep(c(rep("Following Natural Recovery", 3), rep("Following Diagnosis and Recovery",3)),15)

r2$Reinfection <- factor(rep(c("Twelve", "Six", "Three"),30), levels = c("Three", "Six", "Twelve"))


r2 %>% filter(Behavior== "M.F.Concurrency") %>% 
  ggplot(aes(x=Treatment, y=mean, col=Reinfection)) +
  geom_point(size=2) +
  geom_line(aes(x=Treatment, y=mean, group=Reinfection)) + 
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1) +
  facet_wrap(~ReinfType, nrow=1) +
  theme(axis.text.x = element_text(angle = 45)) +
  ylim(0,0.6) +
  ggtitle("Higher Male Concurrency")

r2 %>% filter(Behavior== "Avg.Concurrency") %>% 
  ggplot(aes(x=Treatment, y=mean, col=Reinfection)) +
  geom_point(size=2) +
  geom_line(aes(x=Treatment, y=mean, group=Reinfection)) + 
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1) +
  facet_wrap(~ReinfType, nrow=1) +
  theme(axis.text.x = element_text(angle = 45)) +
  ylim(0,0.6) +
  ggtitle("Average Concurrency")

r2 %>% filter(Behavior== "No.Concurrency") %>% 
  ggplot(aes(x=Treatment, y=mean, col=Reinfection)) +
  geom_point(size=2) +
  geom_line(aes(x=Treatment, y=mean, group=Reinfection)) + 
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1) +
  facet_wrap(~ReinfType, nrow=1) +
  theme(axis.text.x = element_text(angle = 45)) +
  ylim(0,0.6) +
  ggtitle("No Concurrency")

r2 %>% filter(Reinfection=="Three") %>% 
  ggplot(aes(x=Behavior, y=mean, col=Treatment)) +
  geom_point(size=2) +
 # geom_line(aes(x=Behavior, y=mean, group=Treatment)) + 
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1) +
  facet_wrap(~ReinfType, nrow=1)  +
  theme(axis.text.x = element_text(angle = 45)) +
  ylim(0,0.5) +
  ggtitle("Proportion Reinfected within 3 Months of Diagnosis or Previous Infection")
```

### Table 

```{r reinf-male-tab}
kable(r2) %>%
  kable_styling()
```

## Among Diagnosed
```{r reinfdiag}
r3 <- rbind(r, r2)
r3$Sex <- c(rep("Female", 90), rep("Male", 90))

r3 %>% filter(ReinfType=="Following Diagnosis") %>% 
  ggplot(aes(x=Treatment, y=mean, col=Reinfection)) +
  geom_point(size=2) +
 geom_line(aes(x=Treatment, y=mean, group=Reinfection)) + 
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1) +
  facet_wrap(~Sex+Behavior, nrow=2)  +
  theme(axis.text.x = element_text(angle = 45)) +
  ylim(0,0.7)

r3 %>% filter(Reinfection=="Three") %>% 
  ggplot(aes(x=Treatment, y=mean, col=Sex)) +
  geom_point(size=2) +
 geom_line(aes(x=Treatment, y=mean, group=Sex)) + 
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1) +
  facet_wrap(~ReinfType+Behavior, nrow=2)  +
  theme(axis.text.x = element_text(angle = 45)) +
  ylim(0,0.5)
```

## 20-24
```{r, eval=F}
r20 <- rbind(dat0[[3]][[3]], dat02[[3]][[3]], dat03[[3]][[3]],
          dat[[3]][[3]], dat2[[3]][[3]], dat3[[3]][[3]],
           datept[[3]][[3]], dat2ept[[3]][[3]], dat3ept[[3]][[3]],
           datepthigh[[3]][[3]], dat2epthigh[[3]][[3]], dat3epthigh[[3]][[3]],
           datept1[[3]][[3]], dat2ept1[[3]][[3]], dat3ept1[[3]][[3]])

r$Behavior <- rep(c(rep("M.F.Concurrency",6), rep( "Avg.Concurrency",6), rep( "No.Concurrency",6)),5)
r$Behavior <- factor(r$Behavior, levels=c("M.F.Concurrency", "Avg.Concurrency", "No.Concurrency"))

r$Treatment <- c(rep("No Partner Treatment", 18), rep("Low Partner Treatment", 18), rep("Medium Partner Treatment", 18), rep("High Partner Treatment", 18), rep("All Ongoing Partners", 18))

r$Treatment <- factor(r$Treatment, levels = c("No Partner Treatment", "Low Partner Treatment", "Medium Partner Treatment", "High Partner Treatment", "All Ongoing Partners"))

r$ReinfType <- rep(c(rep("W/O Diagnosis", 3), rep("Following Diagnosis",3)),15)

r$Reinfection <- factor(rep(c("Twelve", "Six", "Three"),30), levels = c("Three", "Six", "Twelve"))

m20 <- rbind(dat0[[3]][[4]], dat02[[3]][[4]], dat03[[3]][[4]],
            dat[[3]][[4]], dat2[[3]][[4]], dat3[[3]][[4]],
           datept[[3]][[4]], dat2ept[[3]][[4]], dat3ept[[3]][[4]],
           datepthigh[[3]][[4]], dat2epthigh[[3]][[4]], dat3epthigh[[3]][[4]],
           datept1[[3]][[4]], dat2ept1[[3]][[4]], dat3ept1[[3]][[4]])

r2$Behavior <- rep(c(rep("M.F.Concurrency",6), rep( "Avg.Concurrency",6), rep( "No.Concurrency",6)),5)
r2$Behavior <- factor(r2$Behavior, levels=c("M.F.Concurrency", "Avg.Concurrency", "No.Concurrency"))

r2$Treatment <- c(rep("No Partner Treatment", 18), rep("Low Partner Treatment", 18), rep("Medium Partner Treatment", 18), rep("High Partner Treatment", 18), rep("All Ongoing Partners", 18))

r2$Treatment <- factor(r2$Treatment, levels = c("No Partner Treatment", "Low Partner Treatment", "Medium Partner Treatment", "High Partner Treatment", "All Ongoing Partners"))

r2$ReinfType <- rep(c(rep("W/O Diagnosis", 3), rep("Following Diagnosis",3)),15)

r2$Reinfection <- factor(rep(c("Twelve", "Six", "Three"),30), levels = c("Three", "Six", "Twelve"))

```
```{r}
r20 <- rbind(dat[[3]][[1]], dat[[3]][[3]], 
             dat2[[3]][[1]], dat2[[3]][[3]], 
             dat3[[3]][[1]], dat3[[3]][[3]])

r20$Behavior <- c(rep("M.F.Concurrency",12), 
                  rep( "Avg.Concurrency",12), 
                  rep( "No.Concurrency",12))

r20$Behavior <- factor(r20$Behavior, levels=c("M.F.Concurrency", "Avg.Concurrency", "No.Concurrency"))

r20$Treatment <- rep("Low Partner Treatment", 36)

r20$ReinfType <- rep(c(rep("Following Natural Recovery", 3), rep("Following Diagnosis and Recovery",3)),6)

r20$Reinfection <- factor(rep(c("Twelve", "Six", "Three"),6), levels = c("Three", "Six", "Twelve"))

r20$Age <- rep(c(rep("All", 6), rep("2024",6)),3)

m20 <- rbind(dat[[3]][[2]], dat[[3]][[4]], 
             dat2[[3]][[2]], dat2[[3]][[4]], 
             dat3[[3]][[2]], dat3[[3]][[4]])

m20$Behavior <- c(rep("M.F.Concurrency",12), 
                  rep( "Avg.Concurrency",12), 
                  rep( "No.Concurrency",12))
m20$Behavior <- factor(m20$Behavior, levels=c("M.F.Concurrency", "Avg.Concurrency", "No.Concurrency"))

m20$Treatment <- rep("Low Partner Treatment", 36)

m20$ReinfType <- rep(c(rep("W/O Diagnosis", 3), rep("Following Diagnosis",3)),6)

m20$Reinfection <- factor(rep(c("Twelve", "Six", "Three"),6), levels = c("Three", "Six", "Twelve"))

m20$Age <- rep(c(rep("All", 6), rep("2024",6)),3)

r4 <- rbind(r20, m20)
r4$Sex <- c(rep("Female", 36), rep("Male", 36))

r4 %>% filter(ReinfType=="Following Diagnosis") %>% 
  ggplot(aes(x=Behavior, y=mean, col=Reinfection)) +
  geom_point(size=2) +
 geom_line(aes(x=Behavior, y=mean, group=Reinfection)) + 
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1) +
  facet_wrap(~Sex+Age, nrow=2)  +
  theme(axis.text.x = element_text(angle = 45)) +
  ylim(0,0.8)
```


# Proportion Ever Infected 
cross-sectional - attr at end of sim 

```{r ever-inf}
femaleEver <- rbind(dat0[[4]][[1]], dat[[4]][[1]], datept[[4]][[1]], datepthigh[[4]][[1]], datept1[[4]][[1]], 
                    dat02[[4]][[1]], dat2[[4]][[1]], dat2ept[[4]][[1]], dat2epthigh[[4]][[1]], dat2ept1[[4]][[1]], 
                    dat03[[4]][[1]], dat3[[4]][[1]], dat2ept[[4]][[1]], dat3epthigh[[4]][[1]], dat3ept1[[4]][[1]])

femaleEver$Behavior <- factor(c(rep("M.F.Concurrency", 5), rep("Avg.Concurrency", 5), rep("No.Concurrency", 5)), levels=c("M.F.Concurrency", "Avg.Concurrency", "No.Concurrency"))

femaleEver$Treatment = factor(rep(c("No Partner Treatment", "Low Partner Treatment", "Medium Partner Treatment", "High Partner Treatment", "All Ongoing Partners"),3), levels = c("No Partner Treatment", "Low Partner Treatment", "Medium Partner Treatment", "High Partner Treatment", "All Ongoing Partners"))

maleEver <- rbind(dat0[[4]][[2]], dat[[4]][[2]], datept[[4]][[2]], datepthigh[[4]][[2]], datept1[[4]][[2]], 
                    dat02[[4]][[2]], dat2[[4]][[2]], dat2ept[[4]][[2]], dat2epthigh[[4]][[2]], dat2ept1[[4]][[2]], 
                    dat03[[4]][[2]], dat3[[4]][[2]], dat2ept[[4]][[2]], dat3epthigh[[4]][[2]], dat3ept1[[4]][[2]])

maleEver$Behavior <- factor(c(rep("M.F.Concurrency", 5), rep("Avg.Concurrency", 5), rep("No.Concurrency", 5)), levels=c("M.F.Concurrency", "Avg.Concurrency", "No.Concurrency"))

maleEver$Treatment = factor(rep(c("No Partner Treatment", "Low Partner Treatment", "Medium Partner Treatment", "High Partner Treatment", "All Ongoing Partners"),3), levels = c("No Partner Treatment", "Low Partner Treatment", "Medium Partner Treatment", "High Partner Treatment", "All Ongoing Partners"))

simEver<- rbind(femaleEver, maleEver)
simEver$Sex <- c(rep("Female", 15), rep("Male", 15))

simEver %>% ggplot(aes(x=Treatment, y=mean, col=Sex)) +
  geom_point(size=3) +
  geom_line(aes(x=Treatment, y=mean, group=Sex)) +
  geom_errorbar(aes(ymin=low, ymax=high), width=0.1) +
  facet_wrap(~Behavior) +
  theme(axis.text.x = element_text(angle = 45)) +
  ylim(0,0.35)
```
